---
title: "PlasmidBenchMarkingAnalysisAndFigures"
output: html_document
date: "2026-06-01"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

if (!require("pacman")) install.packages("pacman")
#devtools::install_github("davidsjoberg/ggsankey")
pacman::p_load(
  tidyverse,
  ggplot2,
  readr,
  dplyr,
  data.table,
  scales,
  svglite,
  ggpubr,
  ggtext,
  ggh4x,
  readxl,
  ggsankey
  )
```

# load files

## compute
```{r}
compute <- read.csv("ResultFiles/RunTimeAndRAMUsage.csv") %>%
    mutate(ToolName = case_when(
    ToolName == "MOBSuite" ~ "MOB-suite",
    ToolName == "PlasmidSPAdes" ~ "plasmidSPAdes",
    T ~ ToolName
  ))
compute
```


## quast

```{r}
quast <- list()

quast$spades <- read.csv("ResultFiles/spades_input/AllSamplesQuastResults_2026-02-18_17-06-50.tsv",sep='\t') %>%
  mutate(
    ToolName = case_when(
      ToolName == "PlaScope_assembly" ~ "PlaScope (assembly)",
      ToolName == "PlaScope_reads" ~ "PlaScope (reads)",
      ToolName == "MOBSuite" ~ "MOB-suite",
      ToolName == "PlasmidSPAdes" ~ "plasmidSPAdes",
      T ~ ToolName
    )
  ) %>% 
  mutate(
    ToolName = factor(ToolName,levels=c("HyAsp","MOB-suite","PLASMe","PlaScope (assembly)","PlaScope (reads)","Plasmer","PlasmidHunter","plasmidSPAdes","Platon"))
  )

quast$unicycler <- read.csv("ResultFiles/unicycler_input/AllSamplesQuastResults_2026-02-18_17-01-03.tsv",sep='\t') %>%
  mutate(
    ToolName = case_when(
      ToolName == "PlaScope_assembly" ~ "PlaScope (assembly)",
      ToolName == "PlaScope_reads" ~ "PlaScope (reads)",
      ToolName == "MOBSuite" ~ "MOB-suite",
      ToolName == "PlasmidSPAdes" ~ "plasmidSPAdes",
      T ~ ToolName
    )
  ) %>% 
  mutate(
    ToolName = factor(ToolName,levels=c("HyAsp","MOB-suite","PLASMe","PlaScope (assembly)","PlaScope (reads)","Plasmer","PlasmidHunter","plasmidSPAdes","Platon"))
  )
```


## binary predictions

```{r}
rawbinarypredictions <- list()

rawbinarypredictions$spades <- read.csv("ResultFiles/spades_input/AllBinaryClassifierContigPredictions_2026-02-18_17-06-50.tsv",sep='\t')
#add in PlaScopeAssemblyPrediction column - no predictions are made
rawbinarypredictions$unicycler <- read.csv("ResultFiles/unicycler_input/AllBinaryClassifierContigPredictions_2026-02-18_17-01-03.tsv",sep='\t') %>% 
  mutate(PlaScopeAssemblyPrediction = "")
```

Process binary predictions blastn results
Can just take first value for some columns as they should all the the same
Length -> will be the same for each Query / Subject
Predictions -> will be the same, tool should only produce one prediction per input contig identifier

Filter blast matches to those above 80% identity and total aligned length

```{r}
binarypredictions <- list()

binarypredictions$spades <- rawbinarypredictions$spades %>%
  group_by(SampleID,QueryID,SubjectID) %>%
  summarise(
    QueryLength = first(QueryLength), #should all be the same
    SubjectLength = first(SubjectLength), #should all be the same
    TotalAlignedLength = sum(AlignmentLength),
    AvgIdentity = mean(Identity),
    MOBPrediction = first(MOBPrediction), #should all be the same
    PLASMePrediction = first(PLASMePrediction),
    PlaScopeAssemblyPrediction = first(PlaScopeAssemblyPrediction),
    PlasmerPrediction = first(PlasmerPrediction),
    PlasmidHunterPrediction = first(PlasmidHunterPrediction),
    PlatonPrediction = first(PlatonPrediction),
    SRAssemblerUsed = first(SRAssemblerUsed),
    .groups = 'drop',
    ) %>%
  mutate(
    TotalAlignedPercent = TotalAlignedLength / QueryLength * 100
  ) %>%
  filter(
    AvgIdentity >= 80, #is also filtered at blast match stage
    TotalAlignedPercent >= 80
  )

binarypredictions$unicycler <- rawbinarypredictions$unicycler %>%
  group_by(SampleID,QueryID,SubjectID) %>%
  summarise(
    QueryLength = first(QueryLength), #should all be the same
    SubjectLength = first(SubjectLength), #should all be the same
    TotalAlignedLength = sum(AlignmentLength),
    AvgIdentity = mean(Identity),
    MOBPrediction = first(MOBPrediction), 
    PLASMePrediction = first(PLASMePrediction),
    PlaScopeAssemblyPrediction = first(PlaScopeAssemblyPrediction),
    PlasmerPrediction = first(PlasmerPrediction),
    PlasmidHunterPrediction = first(PlasmidHunterPrediction),
    PlatonPrediction = first(PlatonPrediction),
    SRAssemblerUsed = first(SRAssemblerUsed),
    .groups = 'drop',
    ) %>%
  mutate(
    TotalAlignedPercent = TotalAlignedLength / QueryLength * 100
  ) %>%
  filter(
    AvgIdentity >= 80, #is also filtered at blast match stage
    TotalAlignedPercent >= 80
  )
```


## de novo blast

```{r}
rawdenovoblast <- list()

rawdenovoblast$spades <- read.csv("ResultFiles/spades_input/AllDeNovoToolsBlastResults_2026-02-18_17-06-50.tsv",sep='\t')
rawdenovoblast$unicycler <- read.csv("ResultFiles/unicycler_input/AllDeNovoToolsBlastResults_2026-02-18_17-01-03.tsv",sep='\t')
```

Process de novo blast results

```{r}
denovoblast <- list()


denovoblast$spades <- rawdenovoblast$spades %>%
  group_by(PlasmidTool,SampleID,QueryID,SubjectID) %>%
  summarise(
    QueryLength = first(QueryLength), #should all be the same
    SubjectLength = first(SubjectLength), #should all be the same
    TotalAlignedLength = sum(AlignmentLength),
    AvgIdentity = mean(Identity),
    Prediction = first(Prediction), # should all be the same
    .groups = 'drop',
    ) %>%
  mutate(
    TotalAlignedPercent = TotalAlignedLength / QueryLength * 100
  ) %>%
  filter(
    AvgIdentity >= 80, #is also filtered at blast match stage
    TotalAlignedPercent >= 80
  )

denovoblast$unicycler <- rawdenovoblast$unicycler %>%
  group_by(PlasmidTool,SampleID,QueryID,SubjectID) %>%
  summarise(
    QueryLength = first(QueryLength), #should all be the same
    SubjectLength = first(SubjectLength), #should all be the same
    TotalAlignedLength = sum(AlignmentLength),
    AvgIdentity = mean(Identity),
    Prediction = first(Prediction), # should all be the same
    .groups = 'drop',
    ) %>%
  mutate(
    TotalAlignedPercent = TotalAlignedLength / QueryLength * 100
  ) %>%
  filter(
    AvgIdentity >= 80, #is also filtered at blast match stage
    TotalAlignedPercent >= 80
  )
```

## deadends

from https://github.com/rrwick/GFA-dead-end-counter

```{r}
deadends <- list()
deadends$spades <- read.csv("ResultFiles/spades_input/MetricsAndTyping/AllDeadends_2026-02-18_17-06-50.tab",sep='\t')
deadends$unicycler <- read.csv("ResultFiles/unicycler_input/MetricsAndTyping/AllDeadends_2026-02-18_17-01-03.tab",sep='\t')
```

##coverage

from minimap2 | samtools sort | samtools view | samtools coverage

```{r}
coverage <- read.csv("ResultFiles/spades_input/MetricsAndTyping/AllCoverage.tsv",sep='\t')
coverage %<>%
  separate_wider_delim(
    X.rname,delim = '__',names = c(NA,"Sample_contigID"),cols_remove = F
  ) %>%
  mutate(
    Sample_ChrPl = case_when(
      Sample_contigID == 'chr' ~ "chromosome",
      str_detect(Sample_contigID, regex("pl_[0-9]*",ignore_case = T)) ~ "plasmid"
    )
  ) %>%
  group_by(SampleID) %>%
  mutate(
    meandepthNorm = meandepth / meandepth[Sample_ChrPl == "chromosome"]
  )
coverage
```

## contig sizes

from seqkit fx2tab

```{r}
contigsizes <- list()

contigsizes$spades <- read.csv("ResultFiles/spades_input/MetricsAndTyping/AllInputAssemblyContigSizes_2026-02-18_17-06-50.tsv",sep='\t')
contigsizes$unicycler <- read.csv("ResultFiles/unicycler_input/MetricsAndTyping/AllInputAssemblyContigSizes_2026-02-18_17-01-03.tsv",sep='\t')
```


## input assembly quasts
```{r}
inputassemblyQuast <- list()

inputassemblyQuast$spades <- read.csv("ResultFiles/spades_input/MetricsAndTyping/AllInputAssemblyQuastResults_2026-02-18_17-06-50.tsv", sep='\t')
inputassemblyQuast$unicycler <- read.csv("ResultFiles/unicycler_input/MetricsAndTyping/AllInputAssemblyQuastResults_2026-02-18_17-01-03.tsv",sep='\t')
```


## kleborate AMR
```{r}
klebAMR <- read.csv("ResultFiles/spades_input/MetricsAndTyping/AllKleborateAMR.tsv",sep='\t')
```

Convert to count of kleborate AMR genes per contig

```{r}
klebAMR_countPerContig <- klebAMR %>%
  filter(
    Input_sequence_ID != '-',
    Genetic_variation_type == 'Gene presence detected'
  ) %>%
  group_by(Input_sequence_ID) %>%
  summarise(AMRcount=n())
#klebAMR_countPerContig
```

Need to make summary counts for each Input sequence ID and total plasmid content - summarise into quast reference sequence

```{r}
klebAMR_completeCount <- klebAMR %>%
  filter(
    Input_sequence_ID != '-',
    Genetic_variation_type == 'Gene presence detected'
  ) %>%
  group_by(Input_file_name) %>%
  summarise(AMRcount = n()) %>%
  mutate(Input_sequence_ID = paste(Input_file_name,"__completeAssembly",sep = "")) %>%
  select(Input_sequence_ID,AMRcount)
#klebAMR_completeCount
```


```{r}
klebAMR_allPlasmids <- klebAMR %>%
  filter(
    Input_sequence_ID != '-',
    Genetic_variation_type == 'Gene presence detected'
    ) %>%
  group_by(Input_sequence_ID) %>%
  summarise(count = n()) %>%
separate_wider_delim(
    Input_sequence_ID,delim = '__',names = c('SampleID',"Sample_contigID"),cols_remove = F
  ) %>%
  mutate(
    Sample_ChrPl = case_when(
      Sample_contigID == 'chr' ~ "chromosome",
      str_detect(Sample_contigID, regex("pl_[0-9]*",ignore_case = T)) ~ "plasmid"
    )
  ) %>%
  filter(Sample_ChrPl == 'plasmid') %>%
  group_by(SampleID, Sample_ChrPl) %>%
  summarise(AMRcount = sum(count),.groups = 'drop') %>%
  mutate(
    Input_sequence_ID = paste(SampleID,"__allPlasmids",sep = "")
  ) %>%
  select(Input_sequence_ID,AMRcount)
#klebAMR_allPlasmids
```


```{r}
klebAMRcount <- klebAMR_countPerContig %>%
  add_row(klebAMR_completeCount) %>%
  add_row(klebAMR_allPlasmids)
```

## kelborate other typing

```{r}
klebTyping <- read.csv("ResultFiles/spades_input/MetricsAndTyping/AllKleborateTyping.tsv",sep='\t')
```

## Mash distances

```{r}
#just want to extract distance metrics between plasmids and chromosome
#chr -> all plasmids, individual plasmids, (chromosome)
#map distance to chromosome onto QuastReferenceID in typing
#can just map queryID onto QuastReferenceID with some column renaming
#process shared hashes column? remove /100000
mash <- read.csv("ResultFiles/spades_input/MetricsAndTyping/AllMashDistances.tsv",sep='\t') %>%
  separate_wider_delim(
    shared.hashes,delim = '/100000',names = c("MashSharedHashes(/100000)",NA),cols_remove = F
  ) %>%
  separate_wider_delim(
    query.ID, delim=".fasta",names=c("MashQuerySequence",NA),cols_remove=F
  ) %>%
  select(MashQuerySequence, distance, `MashSharedHashes(/100000)`) %>%
  mutate(
    `MashSharedHashes(/100000)` = as.numeric(`MashSharedHashes(/100000)`)
  ) %>%
  rename(MashDistanceToChr = distance)
mash
```


## Pling and IS

Read pling clustering data (not used) and IS counts from Winkler et al. supp data table

```{r}
Pling_IS <- read_xlsx("Copy of Winkler et al Table S1.xlsx",skip = 1) %>%
  select(sequence_name,strain_ID,pling_community,pling_cluster,num_element_IS)
Pling_IS
```


## NCBI publications

From Pubmed csv download

```{r}
NCBIpubs <- read.csv("ResultFiles/PubMed_Timeline_Results_by_Year.csv",skip=1 )
NCBIpubs
```

## Sankey input

Excel spreadsheet compatible for sankey plotting

```{r}
sankeysheet <- read_excel("ResultFiles/PlasmidSankey.xlsx",sheet = "SankeyVersion")
sankeysheet
```


# Process files

## calculate recall, precision, f1

Metrics missing when no alignment from Quast

```{r}
quastMetrics <- list()

quastMetrics$spades <- quast$spades %>%
  #replace dashes with NA
  mutate_at(
      vars(-X..unaligned.contigs,-Assembly,-QuastReferenceSequence, -ToolName, -QuastType, -SRAssemblerUsed), ~gsub("-",NA,.)
    ) %>%
  #convert fields to numeric, except for unaligned contigs
    mutate_at(
      vars(-X..unaligned.contigs,-Assembly,-QuastReferenceSequence, -ToolName, -QuastType, -SRAssemblerUsed), as.numeric
    ) %>%
  #deal with unaligned contigs columns separately
    mutate(
      unaligned.contigs.num = as.numeric(gsub(".*?([0-9]+).*", "\\1", X..unaligned.contigs))
    ) %>%
  #calculate number of plasmid contigs
    mutate(
      NumPlasmidContigs = X..contigs - unaligned.contigs.num
    ) %>%
  #calculate precision, recall and overall F1 score, and duplicate plasmid length
  #can only calculate precision at plasmidome levels as tools don't create putative plasmid bins
  mutate(
    Precision = case_when(
      QuastType == 'CombinedPlasmids' & !is.na(Total.aligned.length) ~ Total.aligned.length / Total.length.....0.bp.,
      QuastType == 'CombinedPlasmids' & is.na(Total.aligned.length) ~ 0 #set precision to 0 when nothing aligned i.e. not match between predictions and plasmid
    ),
    Recall = case_when(
      QuastType %in% c("CombinedPlasmids","IndividualPlasmids") & !is.na(Total.aligned.length) ~ Genome.fraction.... / 100,
      QuastType %in% c("CombinedPlasmids","IndividualPlasmids") & is.na(Total.aligned.length) ~ 0 #set to 0 when nothing aligned
    ),
    #F1 = (2 * Precision * Recall) / (Precision + Recall), #should only calculate for CombinedPlasmids
    F1 = case_when(
      QuastType == "CombinedPlasmids" & !is.na((2 * Precision * Recall) / (Precision + Recall)) ~ (2 * Precision * Recall) / (Precision + Recall),
      QuastType == "CombinedPlasmids" & is.na((2 * Precision * Recall) / (Precision + Recall)) ~ 0 #set to 0 when precision or recall are 0
    ),
    DuplicatedLength = pmax(Total.aligned.length - Reference.length,0)
  ) %>%
  #fill out missing recall, precision and F1 scores
  #can assume missing values are 0
  #samples with 0 plasmids have no Quast reference sequence and are only present in ChromosomeOnly QuastType
  group_by(QuastType) %>%
  group_modify(~ if (.y$QuastType == 'CombinedPlasmids'){
    complete(.x, QuastReferenceSequence,ToolName,fill=list(F1=0,Precision=0,Recall=0))
  } else {
    .x
  }) %>%
  ungroup() %>%
  #add tool category columns
  mutate(
    ToolType = case_when(
      ToolName %in% c("MOB-suite","Plasmer","PlasmidHunter","Platon","PlaScope (assembly)") ~ "Binary Classifier",
      ToolName %in% c("PlaScope (reads)","plasmidSPAdes","HyAsp") ~ "De Novo Assembler"
    ),
    InputType = case_when(
      ToolName %in% c("MOB-suite","Plasmer","PlasmidHunter","Platon","PlaScope (assembly)","HyAsp","PLASMe") ~ "Assembly Based",
      ToolName %in% c("PlaScope (reads)","plasmidSPAdes") ~ "Read Based"
    )
  ) %>%
  #make sample ID and contig ID columns
  separate_wider_delim(
    QuastReferenceSequence, names = c("SampleID","SampleContigID"), delim = '__', cols_remove = F
  )

quastMetrics$unicycler <- quast$unicycler %>%
  mutate_at(
      vars(-X..unaligned.contigs,-Assembly,-QuastReferenceSequence, -ToolName, -QuastType, -SRAssemblerUsed), ~gsub("-",NA,.) #remove non digit strings e.g. -
    ) %>%
    mutate_at(
      vars(-X..unaligned.contigs,-Assembly,-QuastReferenceSequence, -ToolName, -QuastType, -SRAssemblerUsed), as.numeric #unaligned contigs is in two part string
    ) %>%
    mutate(
      unaligned.contigs.num = as.numeric(gsub(".*?([0-9]+).*", "\\1", X..unaligned.contigs))
    ) %>%
    mutate(
      NumPlasmidContigs = X..contigs - unaligned.contigs.num
    ) %>%
  mutate(
    #can only calculate precision at plasmidome levels, tools don't group sequences into plasmid bins
    #need to check that Total.aligned.length is not NA otherwise precision not calculated
    Precision = case_when(
      QuastType == 'CombinedPlasmids' & !is.na(Total.aligned.length) ~ Total.aligned.length / Total.length.....0.bp.,
      QuastType == 'CombinedPlasmids' & is.na(Total.aligned.length) ~ 0 #set precision to 0 when nothing aligned i.e. not match between predictions and plasmid
    ),
    Recall = case_when(
      QuastType %in% c("CombinedPlasmids","IndividualPlasmids") & !is.na(Total.aligned.length) ~ Genome.fraction.... / 100,
      QuastType %in% c("CombinedPlasmids","IndividualPlasmids") & is.na(Total.aligned.length) ~ 0 #set to 0 when nothing aligned
    ),
    #F1 = (2 * Precision * Recall) / (Precision + Recall), #should only calculate for CombinedPlasmids
    F1 = case_when(
      QuastType == "CombinedPlasmids" & !is.na((2 * Precision * Recall) / (Precision + Recall)) ~ (2 * Precision * Recall) / (Precision + Recall),
      QuastType == "CombinedPlasmids" & is.na((2 * Precision * Recall) / (Precision + Recall)) ~ 0 #set to 0 when precision or recall are 0
    ),
    DuplicatedLength = pmax(Total.aligned.length - Reference.length,0)
  ) %>%
    group_by(QuastType) %>%
  group_modify(~ if (.y$QuastType == 'CombinedPlasmids'){
    complete(.x, QuastReferenceSequence,ToolName,fill=list(F1=0,Precision=0,Recall=0))
  } else {
    .x
  }) %>%
  ungroup() %>%
  mutate(
    ToolType = case_when(
      ToolName %in% c("MOB-suite","Plasmer","PlasmidHunter","Platon","PlaScope (assembly)") ~ "Binary Classifier",
      ToolName %in% c("PlaScope (reads)","plasmidSPAdes","HyAsp") ~ "De Novo Assembler"
    ),
    InputType = case_when(
      ToolName %in% c("MOB-suite","Plasmer","PlasmidHunter","Platon","PlaScope (assembly)","HyAsp","PLASMe") ~ "Assembly Based",
      ToolName %in% c("PlaScope (reads)","plasmidSPAdes") ~ "Read Based"
    )
  ) %>%
  separate_wider_delim(
    QuastReferenceSequence, names = c("SampleID","SampleContigID"), delim = '__', cols_remove = F
  )

```


```{r}
srassembly_metrics <- list()

srassembly_metrics$spades <- inputassemblyQuast$spades %>%
  #filter(QuastType == 'ChromosomeAndPlasmid') %>%
  # separate_wider_delim(
  #   QuastReferenceSequence,delim = '__',names = c("SampleID",NA),cols_remove = F
  # ) %>%
  select(QuastReferenceSequence,X..contigs,auN,auNG,auNA,auNGA,Genome.fraction....,Largest.alignment,Duplication.ratio,Total.aligned.length) %>%
  rename(
      InputContigCount = X..contigs,
      InputauN = auN,
      InputauNG = auNG,
      InputauNA = auNA,
      InputauNGA = auNGA,
      InputGenomeFraction = Genome.fraction....,
      InputLargestAlignment = Largest.alignment,
      InputDuplicationRatio = Duplication.ratio,
      InputTotalAlignedLength = Total.aligned.length
    ) %>%
  mutate(InputType = 'Assembly Based')

srassembly_metrics$unicycler <- inputassemblyQuast$unicycler %>%
  #filter(QuastType == 'ChromosomeAndPlasmid') %>%
  # separate_wider_delim(
  #   QuastReferenceSequence,delim = '__',names = c("SampleID",NA),cols_remove = F
  # ) %>%
  select(QuastReferenceSequence,X..contigs,auN,auNG,auNA,auNGA,Genome.fraction....,Largest.alignment,Duplication.ratio,Total.aligned.length) %>%
  rename(
      InputContigCount = X..contigs,
      InputauN = auN,
      InputauNG = auNG,
      InputauNA = auNA,
      InputauNGA = auNGA,
      InputGenomeFraction = Genome.fraction....,
      InputLargestAlignment = Largest.alignment,
      InputDuplicationRatio = Duplication.ratio,
      InputTotalAlignedLength = Total.aligned.length
    ) %>%
  mutate(InputType = 'Assembly Based')

```


## combine metrics with typing

Not appropriate to combine input assembly metrics for read based tools

```{r}
quastMetricsTyping <- list()

quastMetricsTyping$spades <- quastMetrics$spades %>%
  left_join(srassembly_metrics$spades ,by=join_by(QuastReferenceSequence,InputType)) %>%
  left_join(mash, by=join_by(QuastReferenceSequence == MashQuerySequence )) %>%
  left_join(Pling_IS,by=join_by(QuastReferenceSequence == sequence_name)) %>%
  left_join(deadends$spades,by='SampleID') %>%
  left_join(coverage,by = join_by(QuastReferenceSequence == X.rname)) %>%
  left_join(klebTyping,by=join_by(SampleID.x == strain)) %>%
  left_join(klebAMRcount,by = join_by(QuastReferenceSequence==Input_sequence_ID)) %>%
   mutate(
     AMRcount = replace_na(AMRcount,0)
   )

quastMetricsTyping$unicycler <- quastMetrics$unicycler %>%
  left_join(srassembly_metrics$unicycler,by=join_by(QuastReferenceSequence,InputType)) %>%
  left_join(mash, by=join_by(QuastReferenceSequence == MashQuerySequence )) %>%
  left_join(Pling_IS,by=join_by(QuastReferenceSequence == sequence_name)) %>%
  left_join(deadends$unicycler,by='SampleID') %>%
  left_join(coverage,by = join_by(QuastReferenceSequence == X.rname)) %>%
  left_join(klebTyping,by=join_by(SampleID.x == strain)) %>%
  left_join(klebAMRcount,by = join_by(QuastReferenceSequence==Input_sequence_ID)) %>%
   mutate(
     AMRcount = replace_na(AMRcount,0)
   )
quastMetricsTyping
```



# Input assemby metrics

## Number of blast identified contigs and length

Total length in Mbp

```{r}
denovoblast$spades %>%
  filter(PlasmidTool == 'SRonlyContigs') %>%
  filter(QueryLength > 500 ) %>%
  #count(SampleID,QueryID)
  distinct(SampleID,QueryID,.keep_all = T) %>%
  summarise(len = sum(QueryLength) / 1000000)
```

Number of contigs blast matched to chr and plasmids

```{r}
denovoblast$spades %>%
  filter(PlasmidTool == 'SRonlyContigs') %>%
  separate_wider_delim(
    SubjectID,delim = '__',names = c(NA,"Sample_contigID"),cols_remove = F
  ) %>%
  mutate(
    Sample_ChrPl = case_when(
      Sample_contigID == 'chr' ~ "chromosome",
      str_detect(Sample_contigID, regex("pl_[0-9]*",ignore_case = T)) ~ "plasmid"
    )
  ) %>%
  group_by(SampleID,QueryID) %>%
  mutate(Consistent = case_when(
    all(Sample_ChrPl == 'chromosome') ~ 'chromosome',
    all(Sample_ChrPl == 'plasmid') ~ 'plasmid',
    T ~ 'mixed'
  )) %>%
  ungroup() %>%
  distinct(SampleID,QueryID,.keep_all = T) %>%
  count(Consistent)
```

Total length of matches to chr and plasmid in Mbp

```{r}
denovoblast$spades %>%
  filter(PlasmidTool == 'SRonlyContigs') %>%
  separate_wider_delim(
    SubjectID,delim = '__',names = c(NA,"Sample_contigID"),cols_remove = F
  ) %>%
  mutate(
    Sample_ChrPl = case_when(
      Sample_contigID == 'chr' ~ "chromosome",
      str_detect(Sample_contigID, regex("pl_[0-9]*",ignore_case = T)) ~ "plasmid"
    )
  ) %>%
  group_by(SampleID,QueryID) %>%
  mutate(Consistent = case_when(
    all(Sample_ChrPl == 'chromosome') ~ 'chromosome',
    all(Sample_ChrPl == 'plasmid') ~ 'plasmid',
    T ~ 'mixed'
  )) %>%
  ungroup() %>%
  group_by(Consistent) %>%
  summarise(len = sum(QueryLength) / 1000000)
```



# Plotting colours

```{r}
plasmid.tool.colours <- c(
  "MOB-suite" = '#FF96C8FF',
  "PlaScope (assembly)" = '#783C8CFF',
  "PlaScope (reads)" = '#783C8CFF',
  "Plasmer" = '#506EBEFF',
  "PlasmidHunter" = '#64AA00FF',
  "plasmidSPAdes" = '#FFDC14FF',
  "Platon" = '#FF6400FF',
  "HyAsp" = '#DC0000FF',
  "PLASMe" = '#641414FF',
  "SPAdes" = 'grey30',
  "Unicycler" = 'grey30'
)

plasmid.tool.colours.fill <- c(
  "MOB-suite" = '#FFD6EA',
  "PlaScope (assembly)" = '#E7D4ED',
  "PlaScope (reads)" = '#E7D4ED',
  "Plasmer" = '#D2DAEE',
  "PlasmidHunter" = '#E5FFC2',
  "plasmidSPAdes" = '#FFF3AD',
  "Platon" = '#FFDAC2',
  "HyAsp" = '#FFADAD',
  "PLASMe" = '#EFA9A9',
  "SPAdes" = 'grey80',
  "Unicycler" = 'grey80'
)
```

# Figure 2 - pubs and tools per year and sankey

```{r}
plot.pubsPerYear <- NCBIpubs %>%
  filter(Year != 2026) %>%
  ggplot(aes(x=Year,y=Count)) +
  geom_col(fill = '#66c2a5') +
  theme_bw() +
  labs(
    y="Count of Publications in PubMed",
    x = "Year of Publication"
  )
plot.pubsPerYear
```

```{r}
plot.toolsPerYear <- sankeysheet %>%
  ggplot(aes(PubOrReleaseYear)) +
  geom_histogram(binwidth = 1,fill='#8da0cb') +
  labs(
    y='Count of Tools',
    x='Year of Publication or First Release'
  ) +
  theme_bw() +
  scale_y_continuous(breaks=c(0,2,4,6,8,10))
plot.toolsPerYear
```


```{r}
sankeylevels <- c(
      "All Tools",
      "Predicts Plasmids",
      "Illumina Data",
      "Single Isolate Klebsiella",
      "Command Line",
      "Successful Install",
      "Successful Run",
      "Included",
      "Not Relevant",
      "Plasmid Typing",
      "Long Read Required",
      "Metagenomic",
      "E. coli Only",
      "No Command Line",
      "Not available",
      #"Conda Install\n Failed",
      "Install Failed",
      "Docker Only",
      "License Required",
      "No Instructions",
      "Failed Run",
      "Requires Custom Database",
      "Excluded"
    )

sankeylevels.colours <- c(
      "All Tools"='#90CAF9',
      "Predicts Plasmids"='#64B5F6',
      "Illumina Data"='#42A5F5',
      "Single Isolate Klebsiella"='#2196F3',
      "Command Line"='#1E88E5',
      "Successful Install"='#1976D2',
      "Successful Run"='#1565C0',
      "Included"='#0D47A1',
      "Not Relevant"='#fb6a4a',
      "Plasmid Typing" = "#fb6a4a",
      "Long Read Required"='#fb6a4a',
      "Metagenomic"='#fb6a4a',
      "E. coli Only"='#fb6a4a',
      "No Command Line"='#fb6a4a',
      "Not available"='#fb6a4a',
      #"Conda Install\n Failed",
      "Install Failed"='#fb6a4a',
      "Docker Only" = "#fb6a4a",
      "License Required" = "#fb6a4a",
      "No Instructions" = "#fb6a4a",
      "Failed Run" = '#fb6a4a',
      "Requires Custom Database" = "#fb6a4a",
      "Excluded"='#fb6a4a'
    )

plot.toolSankey <- sankeysheet %>%
  make_long(-Tools,-Input,-PubOrReleaseYear) %>%
  mutate(
    node = factor(node,levels = sankeylevels),
    next_node = factor(next_node,levels = sankeylevels)
  ) %>%
  filter(!is.na(node)) %>%
  ggplot(aes(x = x, 
               next_x = next_x, 
               node = node, 
               next_node = next_node,
               fill = factor(node),
             label=node)) +
  geom_sankey(flow.alpha=0.5) +
  geom_sankey_label(color = "white",hjust=0.5,vjust=1.5,size=3,angle=90) +
  theme_sankey() +
  scale_fill_manual(values = sankeylevels.colours) +
    scale_x_discrete(labels = function(x) str_wrap(x, width = 10),expand = expansion(mult = c(0.025,0.05))) +
  scale_y_continuous(expand = expansion(mult = c(0,0.1))) +
    theme(
      legend.position = 'none',
      axis.title.x = element_blank(),
      axis.text.x = element_text(size = 10,face = 'bold')
      ) +
    theme(plot.margin = margin(0.1,0.1,0.1,0.1, "cm"))
plot.toolSankey
#ggsave("Figures/ToolSankey.pdf",dpi=300,units='cm',height = 15,width = 25)
```

Edit figure separately to rotate boxes and add numbers

```{r}
plot.pubToolsPerYear <- ggarrange(
  plot.pubsPerYear,
  plot.toolsPerYear,
  ncol=2,
  align = 'h'
) +
  theme(plot.margin = margin(0.1,0.1,0.1,0.1, "cm"))
plot.pubToolsPerYear
```

```{r}
plot.SankeyToolPubYear <- ggarrange(
  plot.pubToolsPerYear,
  plot.toolSankey,
  nrow=2,
  heights=c(0.65,1)
)
plot.SankeyToolPubYear
#ggsave("Figures/PubsToolsPerYearSankey.pdf",dpi=500,units = 'cm',width=20,height = 20)
```


# Figure 3 - usage plots

## run time numbers

```{r}
compute %>%
  group_by(ToolName) %>%
  summarise(
    m = median(total_minutes,na.rm = T),
    lq = quantile(total_minutes,0.25),
    uq = quantile(total_minutes,0.75)
  )
```

## runtime plot

```{r}
breaks <- 10^(-10:10)
minor_breaks <- rep(1:9, 21)*(10^rep(-10:10, each=9))

plot.runtime <- compute %>%
  mutate(
    ToolType = case_when(
      ToolName %in% c("MOB-suite","Plasmer","PlasmidHunter","Platon","PlaScope (assembly)","HyAsp") ~ "Binary Classifiers",
      ToolName %in% c("PlaScope (reads)","plasmidSPAdes") ~ "De Novo Assemblers"
    ),
    ToolInput = case_when(
      ToolName %in% c("SPAdes","Unicycler") ~ "Genome Assembler",
      ToolName %in% c("MOB-suite","Plasmer","PlasmidHunter","Platon","PlaScope (assembly)","HyAsp","PLASMe") ~ "Assembly-Based",
      ToolName %in% c("PlaScope (reads)","plasmidSPAdes") ~ "Read-Based"
    )
  ) %>%
  ggplot(aes(x=ToolName,y=total_minutes,fill = ToolName,colour = ToolName)) +
  geom_boxplot() +
  scale_y_log10(breaks = breaks, minor_breaks = minor_breaks) +
  #scale_y_continuous(trans='log10') +
  #guides(y='axis_logticks') +
  #coord_trans(y='log10') +
  scale_fill_manual(values = plasmid.tool.colours.fill) +
  scale_color_manual(values = plasmid.tool.colours)+
  labs(y="Total Runtime (minutes)") +
  theme_bw() +
  theme(
    legend.position = 'None',
    axis.title.x = element_blank(),
        panel.grid.major.x = element_blank()
    ) +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))+
  facet_grid(cols = vars(ToolInput),scales = 'free_x',space='free_x')
plot.runtime
#ggsave("Figures/RunTime.pdf",dpi=300,units='cm',height = 8,width = 14)
```


## peak ram numbers

```{r}
compute %>%
  group_by(ToolName) %>%
  summarise(
    m = median(peak_rss_gb,na.rm = T),
    lq = quantile(peak_rss_gb,0.25,na.rm=T),
    uq = quantile(peak_rss_gb,0.75,na.rm=T)
  )
```

## peak ram plot

```{r}
plot.RAM <- compute %>%
  mutate(
    ToolType = case_when(
      ToolName %in% c("MOB-suite","Plasmer","PlasmidHunter","Platon","PlaScope (assembly)","HyAsp") ~ "Binary Classifiers",
      ToolName %in% c("PlaScope (reads)","plasmidSPAdes") ~ "De Novo Assemblers"
    ),
    ToolInput = case_when(
      ToolName %in% c("SPAdes","Unicycler") ~ "Genome Assembler",
      ToolName %in% c("MOB-suite","Plasmer","PlasmidHunter","Platon","PlaScope (assembly)","HyAsp","PLASMe") ~ "Assembly-Based",
      ToolName %in% c("PlaScope (reads)","plasmidSPAdes") ~ "Read-Based"
    )
  ) %>%
  ggplot(aes(x=ToolName,y=peak_rss_gb,fill = ToolName,colour = ToolName)) +
  geom_boxplot() +
  #scale_y_log10(breaks = breaks, minor_breaks = minor_breaks) +
  #scale_y_continuous(trans='log10') +
  #guides(y='axis_logticks') +
  #coord_trans(y='log10') +
  scale_fill_manual(values = plasmid.tool.colours.fill) +
  scale_colour_manual(values = plasmid.tool.colours) +
  labs(y="Peak Memory Usage (GB)") +
  theme_bw() +
  theme(
    legend.position = 'None',
    axis.title.x = element_blank(),
    panel.grid.major.x = element_blank(),
    ) +
    scale_x_discrete(labels = function(x) str_wrap(x, width = 10))+
  facet_grid(cols = vars(ToolInput),scales = 'free_x',space='free_x')
plot.RAM
#ggsave("Figures/PeakRAMUsage.pdf")
```

## Multipanel runtime plot

```{r}
ggarrange(
  plot.runtime,
  plot.RAM,
  nrow=2,
  labels = 'AUTO',
  align = 'hv'
)
#ggsave("Figures/Figure3_raw.pdf",dpi=300,units = 'cm',width = 25,height = 20)
```


# Table 2 - TPFPTNFN

## Numbers

```{r}
#total number of contigs - spades
contigsizes$spades %>% nrow()
```

```{r}
#total number of contigs - unicycler
contigsizes$unicycler %>% nrow()
```


Number of classifications for tools - binary

Not all contigs for SPAdes and Unicycler could be blast matched

Correct Incorrect for binary tools
```{r}
TPFPTNFN <- list()

TPFPTNFN$spades <- binarypredictions$spades %>%
  separate_wider_delim(
    SubjectID,delim = '__',names = c(NA,"Sample_contigID"),cols_remove = F
  ) %>%
    mutate(
    Sample_ChrPl = case_when(
      Sample_contigID == 'chr' ~ "chromosome",
      str_detect(Sample_contigID, regex("pl_[0-9]*",ignore_case = T)) ~ "plasmid"
    )
    ) %>%
  group_by(SampleID,QueryID) %>%
  mutate(
    ConsistentTruth = case_when(
      all(Sample_ChrPl == 'chromosome') ~ 'chromosome',
      all(Sample_ChrPl == 'plasmid') ~ 'plasmid',
      T ~ 'mixed' #classify anything else as mixed
    )
  ) %>%
  ungroup() %>%
  distinct(SampleID,QueryID,.keep_all = T)  %>%
  #filter(QueryLength > 500) %>%
  select(SampleID,PlatonPrediction,PlasmidHunterPrediction,PlasmerPrediction,MOBPrediction,PlaScopeAssemblyPrediction,PLASMePrediction,ConsistentTruth) %>%
  pivot_longer(
    cols = c(PlasmerPrediction, PlasmidHunterPrediction, MOBPrediction, PlatonPrediction,PlaScopeAssemblyPrediction,PLASMePrediction),
    names_to = "Tool",
    values_to = "ToolPrediction"
  ) %>%
  mutate(
    Tool = case_when(
      Tool == "PlasmerPrediction" ~ "Plasmer",
      Tool == "PlasmidHunterPrediction" ~ "PlasmidHunter",
      Tool == "MOBPrediction" ~ "MOB-suite",
      Tool == "PlatonPrediction" ~ "Platon",
      Tool == "PlaScopeAssemblyPrediction" ~ "PlaScope (assembly)",
      Tool == 'PLASMePrediction' ~ 'PLASMe'
    )
  ) %>%
  group_by(Tool) %>%
  summarise(
    total_rows = n(),
    `Plasmid Predicted - Plasmid Blast` = sum((ToolPrediction=='plasmid') & (ConsistentTruth == 'plasmid')),
    `Plasmid Predicted - Chromosome Blast` = sum((ToolPrediction=='plasmid') & (ConsistentTruth == 'chromosome')),
    `Plasmid Predicted - Mixed Blast` = sum((ToolPrediction == 'plasmid') & (ConsistentTruth == 'mixed')),
    `Chromosome Predicted - Plasmid Blast` = sum((ToolPrediction=='chromosome') & (ConsistentTruth == 'plasmid')),
    `Chromosome Predicted - Chromosome Blast` = sum((ToolPrediction=='chromosome') & (ConsistentTruth == 'chromosome')),
    `Chromosome Predicted - Mixed Blast` = sum((ToolPrediction=='chromosome') & (ConsistentTruth == 'mixed')),
    #Incorrect = sum((ToolPrediction != ConsistentTruth) & (ToolPrediction != ""), na.rm = TRUE),
    #`No Classification` = sum(ToolPrediction == ""),
    `No Classification - Plasmid Blast` = sum((ToolPrediction %in% c("","shorter_than_500")) & (ConsistentTruth == 'plasmid')),
    `No Classification - Chromosome Blast` = sum((ToolPrediction %in% c("","shorter_than_500")) & (ConsistentTruth == 'chromosome')),
    `No Classification - Mixed Blast` = sum((ToolPrediction %in% c("","shorter_than_500")) & (ConsistentTruth == 'mixed')),
    .groups = 'drop'
  ) 

TPFPTNFN$unicycler <- binarypredictions$unicycler %>%
  separate_wider_delim(
    SubjectID,delim = '__',names = c(NA,"Sample_contigID"),cols_remove = F
  ) %>%
    mutate(
    Sample_ChrPl = case_when(
      Sample_contigID == 'chr' ~ "chromosome",
      str_detect(Sample_contigID, regex("pl_[0-9]*",ignore_case = T)) ~ "plasmid"
    )
    ) %>%
  group_by(SampleID,QueryID) %>%
  mutate(
    ConsistentTruth = case_when(
      all(Sample_ChrPl == 'chromosome') ~ 'chromosome',
      all(Sample_ChrPl == 'plasmid') ~ 'plasmid',
      T ~ 'mixed' #classify anything else as mixed
    )
  ) %>%
  ungroup() %>%
  distinct(SampleID,QueryID,.keep_all = T)  %>%
  #filter(QueryLength > 500) %>%
  select(SampleID,PlatonPrediction,PlasmidHunterPrediction,PlasmerPrediction,MOBPrediction,PlaScopeAssemblyPrediction,PLASMePrediction,ConsistentTruth) %>%
  pivot_longer(
    cols = c(PlasmerPrediction, PlasmidHunterPrediction, MOBPrediction, PlatonPrediction,PlaScopeAssemblyPrediction,PLASMePrediction),
    names_to = "Tool",
    values_to = "ToolPrediction"
  ) %>%
  mutate(
    Tool = case_when(
      Tool == "PlasmerPrediction" ~ "Plasmer",
      Tool == "PlasmidHunterPrediction" ~ "PlasmidHunter",
      Tool == "MOBPrediction" ~ "MOB-suite",
      Tool == "PlatonPrediction" ~ "Platon",
      Tool == "PlaScopeAssemblyPrediction" ~ "PlaScope (assembly)",
      Tool == 'PLASMePrediction' ~ 'PLASMe'
    )
  ) %>%
  group_by(Tool) %>%
  summarise(
    total_rows = n(),
    `Plasmid Predicted - Plasmid Blast` = sum((ToolPrediction=='plasmid') & (ConsistentTruth == 'plasmid')),
    `Plasmid Predicted - Chromosome Blast` = sum((ToolPrediction=='plasmid') & (ConsistentTruth == 'chromosome')),
    `Plasmid Predicted - Mixed Blast` = sum((ToolPrediction == 'plasmid') & (ConsistentTruth == 'mixed')),
    `Chromosome Predicted - Plasmid Blast` = sum((ToolPrediction=='chromosome') & (ConsistentTruth == 'plasmid')),
    `Chromosome Predicted - Chromosome Blast` = sum((ToolPrediction=='chromosome') & (ConsistentTruth == 'chromosome')),
    `Chromosome Predicted - Mixed Blast` = sum((ToolPrediction=='chromosome') & (ConsistentTruth == 'mixed')),
    #Incorrect = sum((ToolPrediction != ConsistentTruth) & (ToolPrediction != ""), na.rm = TRUE),
    #`No Classification` = sum(ToolPrediction == ""),
    `No Classification - Plasmid Blast` = sum((ToolPrediction %in% c("","shorter_than_500")) & (ConsistentTruth == 'plasmid')),
    `No Classification - Chromosome Blast` = sum((ToolPrediction %in% c("","shorter_than_500")) & (ConsistentTruth == 'chromosome')),
    `No Classification - Mixed Blast` = sum((ToolPrediction %in% c("","shorter_than_500")) & (ConsistentTruth == 'mixed')),
    .groups = 'drop'
  ) 
```


```{r}
TPFPTNFN$spades
```


```{r}
TPFPTNFN$unicycler
```

Numbers for de novo assembly tools

```{r}
denovoblast$spades %>%
  filter(PlasmidTool != "SRonlyContigs") %>%
  separate_wider_delim(
    SubjectID,delim = '__',names = c(NA,"Sample_contigID"),cols_remove = F
  ) %>%
  mutate(
    Sample_ChrPl = case_when(
      Sample_contigID == 'chr' ~ "chromosome",
      str_detect(Sample_contigID, regex("pl_[0-9]*",ignore_case = T)) ~ "plasmid"
    ),
    ToolPrediction = Prediction
  ) %>%
  group_by(SampleID,QueryID) %>%
  mutate(
    ConsistentTruth = case_when(
      all(Sample_ChrPl == 'chromosome') ~ 'chromosome',
      all(Sample_ChrPl == 'plasmid') ~ 'plasmid',
      T ~ 'mixed'
  )) %>%
  ungroup() %>%
  distinct(SampleID,QueryID,.keep_all = T) %>%
  group_by(PlasmidTool) %>%
  summarise(
    total_rows = n(),
    `Plasmid Predicted - Plasmid Blast` = sum((ToolPrediction=='plasmid') & (ConsistentTruth == 'plasmid')),
    `Plasmid Predicted - Chromosome Blast` = sum((ToolPrediction=='plasmid') & (ConsistentTruth == 'chromosome')),
    `Plasmid Predicted - Mixed Blast` = sum((ToolPrediction == 'plasmid') & (ConsistentTruth == 'mixed')),
     `Chromosome Predicted - Plasmid Blast` = sum((ToolPrediction=='chromosome') & (ConsistentTruth == 'plasmid')),
     `Chromosome Predicted - Chromosome Blast` = sum((ToolPrediction=='chromosome') & (ConsistentTruth == 'chromosome')),
     `Chromosome Predicted - Mixed Blast` = sum((ToolPrediction=='chromosome') & (ConsistentTruth == 'mixed')),
    #Incorrect = sum((ToolPrediction != ConsistentTruth) & (ToolPrediction != ""), na.rm = TRUE),
    `No Classification` = sum(ToolPrediction == ""),
    `No Classification - Plasmid Blast` = sum((ToolPrediction == "") & (ConsistentTruth == 'plasmid')),
    `No Classification - Chromosome Blast` = sum((ToolPrediction == "") & (ConsistentTruth == 'chromosome')),
    `No Classification - Mixed Blast` = sum((ToolPrediction == "") & (ConsistentTruth == 'mixed')),
    .groups = 'drop'
            )
```

# Figure 4 - Precision / Recall

## Numbers

Plasmidome precision - SPAdes
```{r}
quastMetricsTyping$spades %>%
  filter(QuastType == 'CombinedPlasmids') %>%
  group_by(ToolName) %>%
  summarise(
    med = median(Precision,na.rm = T),
    lq = quantile(Precision,0.25,na.rm = T),
    uq = quantile(Precision,0.75,na.rm = T),
    min = min(Precision,na.rm = T),
    max = max(Precision,na.rm = T)
  ) %>%
  arrange(med)
```


Plasmidome recall - SPAdes
```{r}
quastMetricsTyping$spades %>%
  filter(QuastType == 'CombinedPlasmids') %>%
  group_by(ToolName) %>%
  summarise(
    med = median(Recall,na.rm = T),
    lq = quantile(Recall,0.25,na.rm = T),
    uq = quantile(Recall,0.75,na.rm = T),
    min = min(Recall,na.rm = T),
    max = max(Recall,na.rm = T)
  ) %>%
  arrange(med)
```

Plasmidome F1 - SPAdes
```{r}
quastMetricsTyping$spades %>%
  filter(QuastType == 'CombinedPlasmids') %>%
  group_by(ToolName) %>%
  summarise(
    med = median(F1,na.rm = T),
    lq = quantile(F1,0.25,na.rm = T),
    uq = quantile(F1,0.75,na.rm = T),
    min = min(F1,na.rm = T),
    max = max(F1,na.rm = T)
  ) %>%
  arrange(med)
```



## Plots

Plasmidome recall - SPAdes
```{r}
plot.quast.recall.spades <- quastMetricsTyping$spades %>%
  filter(QuastType == 'CombinedPlasmids') %>% #isolate level
  ggplot(aes(x=ToolName,y=Recall,fill=ToolName,colour=ToolName)) +
  geom_boxplot() +
  scale_fill_manual(values = plasmid.tool.colours.fill) +
  scale_color_manual(values= plasmid.tool.colours) +
  ylim(-0.05,1) +
  theme_bw() +
  theme(
    legend.position = 'None',
    axis.title.x = element_blank(),
        panel.grid.major.x = element_blank()
    ) +
  labs(y="Recall - Total Plasmid Content") +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))+
  facet_grid(cols = vars(InputType),scales = 'free_x',space='free_x')
plot.quast.recall.spades
#ggsave("Figures/ToolRecall.pdf",dpi = 300,units = 'cm',width=14,height = 8)
```

Plasmidome precision - SPAdes
```{r}
plot.quast.precision.spades <- quastMetricsTyping$spades %>%
  filter(QuastType == 'CombinedPlasmids') %>% #isolate level
  ggplot(aes(x=ToolName,y=Precision,fill=ToolName,colour=ToolName)) +
  geom_boxplot() +
  scale_fill_manual(values = plasmid.tool.colours.fill) +
  scale_color_manual(values = plasmid.tool.colours) +
  ylim(-0.05,1) +
  theme_bw() +
  theme(
    legend.position = 'None',
    axis.title.x = element_blank(),
        panel.grid.major.x = element_blank()
    ) +
  labs(y="Precision - Total Plasmid Content") +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))+
  facet_grid(cols = vars(InputType),scales = 'free_x',space='free_x')
plot.quast.precision.spades
#ggsave("Figures/ToolPrecision.pdf",dpi = 300,units = 'cm',width=14,height = 8)
```

Plasmidome F1 - SPAdes
```{r}
plot.quast.f1.spades <- quastMetricsTyping$spades %>%
  filter(QuastType == 'CombinedPlasmids') %>% #isolate level
  ggplot(aes(x=ToolName,y=F1,fill=ToolName,colour = ToolName)) +
  geom_boxplot() +
  scale_fill_manual(values = plasmid.tool.colours.fill) +
  scale_color_manual(values = plasmid.tool.colours) +
  ylim(-0.05,1) +
  theme_bw() +
  theme(
    legend.position = 'None',
    axis.title.x = element_blank(),
        panel.grid.major.x = element_blank()
    ) +
  labs(y="F1 - Total Plasmid Content") +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))+
  facet_grid(cols = vars(InputType),scales = 'free_x',space='free_x')
plot.quast.f1.spades
#ggsave("Figures/ToolF1.pdf",dpi = 300,units = 'cm',width=14,height = 8)
```

Combined plot - SPAdes
```{r}
plot.fig3.spades <-  ggarrange(
  plot.quast.precision.spades,# + rremove('x.text') +rremove('x.ticks'),
  plot.quast.recall.spades,# + rremove('x.text')+rremove('x.ticks'),
  plot.quast.f1.spades,
  nrow=3,
  align='hv',
  labels = 'AUTO'
)
#ggsave("Figures/Figure4_raw.pdf",plot.fig3.spades,dpi=300,units = 'cm',height = 25,width = 20)
plot.fig3.spades
```

#Stats tests

```{r}
spadesTest <- quastMetricsTyping$spades %>%
  filter(QuastType == 'CombinedPlasmids')
unicyclerTest <- quastMetricsTyping$unicycler %>%
  filter(QuastType == 'CombinedPlasmids')
```


```{r}
test_result <- pairwise.wilcox.test(
  x = spadesTest$F1,
  g = spadesTest$ToolName,
  paired = TRUE,
  p.adjust.method = "bonferroni", 
  exact  = FALSE
) 

p_matrix <- test_result$p.value
df_out <- data.frame(
  Group1 = rownames(p_matrix)[row(p_matrix)],
  Group2 = colnames(p_matrix)[col(p_matrix)],
  p_value = c(p_matrix)
) %>%
  filter(!is.na(p_value)) #remove redundant pairs

#add median and mean F1 differences
pair_diffs <- df_out %>%
  rowwise() %>%
  mutate(
    median_diff = {
      wide <- spadesTest %>%
        mutate(ToolName = as.character(ToolName)) %>%
        filter(ToolName %in% c(Group1, Group2)) %>%
        select(QuastReferenceSequence, ToolName, F1) %>%
        pivot_wider(names_from = ToolName, values_from = F1)
      
      median(wide[[Group1]] - wide[[Group2]], na.rm = TRUE)
    }
  ) %>%
  ungroup()

pair_diffs 
```

```{r}
test_result <- pairwise.wilcox.test(
  x = unicyclerTest$F1,
  g = unicyclerTest$ToolName,
  paired = TRUE,
  p.adjust.method = "bonferroni", 
  exact  = FALSE
) 

p_matrix <- test_result$p.value
df_out <- data.frame(
  Group1 = rownames(p_matrix)[row(p_matrix)],
  Group2 = colnames(p_matrix)[col(p_matrix)],
  p_value = c(p_matrix)
) %>%
  filter(!is.na(p_value)) #remove redundant pairs

#add median and mean F1 differences
pair_diffs <- df_out %>%
  rowwise() %>%
  mutate(
    median_diff = {
      wide <- unicyclerTest %>%
        mutate(ToolName = as.character(ToolName)) %>%
        filter(ToolName %in% c(Group1, Group2)) %>%
        select(QuastReferenceSequence, ToolName, F1) %>%
        pivot_wider(names_from = ToolName, values_from = F1)
      
      median(wide[[Group1]] - wide[[Group2]], na.rm = TRUE)
    }
  ) %>%
  ungroup()

pair_diffs
```



# Poor recall plasmids

Identify plasmids that have no AMR / IS / Kmer sharing and still have low recall with at least one of the best tools

```{r}
quastMetricsTyping$spades %>%
    filter(
    Recall < 0.05, 
    ToolName %in% c("MOB-suite","PlaScope (assembly)","PlaScope (reads)"),
    QuastType == 'IndividualPlasmids',
    AMRcount==0, num_element_IS==0, `MashSharedHashes(/100000)`==0
  ) %>%
  count(QuastReferenceSequence)
```

Get plasmids that performed badly across all the best tools

```{r}
lowrecallplasmids <- quastMetricsTyping$spades %>%
    filter(
    Recall < 0.05, 
    ToolName %in% c("MOB-suite","PlaScope (assembly)","PlaScope (reads)"),
    QuastType == 'IndividualPlasmids',
    AMRcount==0, num_element_IS==0, `MashSharedHashes(/100000)`==0
  ) %>%
  select(SampleID.x,QuastReferenceSequence,ToolName,Recall) %>%
  pivot_wider(names_from = ToolName, values_from = Recall) %>%
  drop_na() #NA's present due to pivoting, meaning recall >0.05 for one of the tools
lowrecallplasmids
```

Pull out plasmid sequences and blast against plasmid tool databases

Link to MOB suite database found on github https://github.com/phac-nml/mob-suite
PlaScope database is downloaded as part of Nextflow setup (from https://zenodo.org/records/1311647/files/Klebsiella_PlaScope.tar.gz)

```
tail -n +2 LowRecallPlasmids.csv | while IFS=',' read -r -a row ; do seqkit grep -p ${row[1]} NorwayData/complete_genomes/${row[0]}.fasta ; done
blastn -query LowRecallPlasmids.fna -subject ncbi_plasmid_full_seqs.fas -outfmt "6 qseqid qlen qstart qend sseqid slen sstart send length pident qcovhsp" > LowRecallPlasmidsMOBDBBlast.out
blastn -query LowRecallPlasmids.fna -subject Nextflow/assets/Klebsiella_PlaScope/DB.fna -outfmt "6 qseqid qlen qstart qend sseqid slen sstart send length pident qcovhsp" > LowRecallPlasmidsPlaScopeDBBlast.out
cat LowRecallPlasmidsMOBDBBlast.out | sed 1i"QueryID\tQueryLength\tQueryStart\tQueryEnd\tSubjectID\tSubjectLength\tSubjectStart\tSubjectEnd\tAlignmentLength\tIdentity\tQCovHSP" > LowRecallPlasmidsMOBDBBlast.outHeader.out
cat LowRecallPlasmidsPlaScopeDBBlast.out | sed 1i"QueryID\tQueryLength\tQueryStart\tQueryEnd\tSubjectID\tSubjectLength\tSubjectStart\tSubjectEnd\tAlignmentLength\tIdentity\tQCovHSP" > LowRecallPlasmidsPlaScopeDBBlast.outHeader.out
```


```{r}
MOBDB <- read.csv("PoorPlasmidsMOBDBBlastHeader.out",sep='\t')
PlaScopeDB <- read.csv("PoorPlasmidsPlaScopeDBBlastHeader.out",sep='\t')
```


```{r}
MOBDB %>%
  mutate(
    TotalAlignedPercent = AlignmentLength / QueryLength * 100
  ) %>%
  left_join(poorplasmids,by=join_by(QueryID == QuastReferenceSequence)) %>%
  group_by(QueryID) %>%
  slice_max(
    order_by = TotalAlignedPercent,
    n = 1,
    with_ties = TRUE   # keep ties then re slice
  ) %>%
  slice_max(
    order_by = Identity,
    n = 1,
    with_ties = FALSE
  ) %>%
  ungroup() %>%
  write_csv("MOBDB_lowrecall_plasmids_filtered.csv")
```

```{r}
PlaScopeDB %>%
  mutate(
    TotalAlignedPercent = AlignmentLength / QueryLength * 100
  ) %>%
  left_join(lowrecallplasmids,by=join_by(QueryID == QuastReferenceSequence)) %>%
  filter(
    #Identity >= 50, 
    #TotalAlignedPercent >= 50,
    QueryID %in% badinboth
  ) %>% 
  group_by(QueryID) %>%
  slice_max(
    order_by = TotalAlignedPercent,
    n = 1,
    with_ties = TRUE   # keep ties then re slice
  ) %>%
  slice_max(
    order_by = Identity,
    n = 1,
    with_ties = FALSE
  ) %>%
  ungroup() %>%
  write_csv("PlaScopeDB_lowrecall_plasmids_filtered.csv")
```


# Supp figures
## Input assembly quality

Numbers

Unicycler total contig number

```{r}
contigsizes$unicycler %>% nrow()
```

Unicycler total contig number over 500bp

```{r}
contigsizes$unicycler %>% 
  filter(length > 500) %>% nrow()
```

SPAdes median auNGA

```{r}
inputassemblyQuast$spades %>%
  filter(QuastType == 'ChromosomeAndPlasmid') %>%
  summarise(median(auNGA))
```

Unicycler median auNGA

```{r}
inputassemblyQuast$unicycler %>%
  filter(QuastType == 'ChromosomeAndPlasmid') %>%
  summarise(median(auNGA))
```

SPAdes contig size histogram

```{r}
plot.AssIn.contiglength.spades <- contigsizes$spades %>%
  filter(AssemblyType == 'SROnlyAssembly') %>%
  mutate(
    SizeBin = cut(length,breaks=c(
      0,
      500,
      1000,
      5000,
      10000,
      50000,
      100000,
      500000,
      1000000,
      5000000
    ),
    labels = c(
      "<500bp",
      "500bp\nto 999bp",
      "1kbp\nto 4.9kbp",
      "5kbp\nto 9.9kbp",
      "10kbp\nto 49.9kbp",
      "50kbp\nto 99.9Kbp",
      "100kbp\nto 499.9kbp",
      "0.5Mbp\nto 0.99Mbp",
      "1Mbp\nto 4.9Mbp"
    ))
  ) %>%
  ggplot(aes(x=SizeBin)) +
  geom_bar(stat="count",fill='#fdb462') +
  theme_bw() +
  labs(
    x="Contig Length",
    y="Count",
    title = "SPAdes Assemblies - Contig Lengths"
  ) +
  theme(axis.text.x = element_text(angle=90,hjust=1, vjust=0.5))
plot.AssIn.contiglength.spades
```

Unicycler contig size histogram

```{r}
plot.AssIn.contiglength.unicycler <- contigsizes$unicycler %>%
  filter(AssemblyType == 'SROnlyAssembly') %>%
  mutate(
    SizeBin = cut(length,breaks=c(
      0,
      500,
      1000,
      5000,
      10000,
      50000,
      100000,
      500000,
      1000000,
      5000000
    ),
    labels = c(
      "<500bp",
      "500bp\nto 999bp",
      "1kbp\nto 4.9kbp",
      "5kbp\nto 9.9kbp",
      "10kbp\nto 49.9kbp",
      "50kbp\nto 99.9Kbp",
      "100kbp\nto 499.9kbp",
      "0.5Mbp\nto 0.99Mbp",
      "1Mbp\nto 4.9Mbp"
    ))
  ) %>%
  ggplot(aes(x=SizeBin)) +
  geom_bar(stat="count",fill='#bebada') +
  theme_bw() +
  labs(
    x="Contig Length",
    y="Count",
    title = "Unicycler Assemblies - Contig Lengths"
  ) +
  theme(axis.text.x = element_text(angle=90,hjust=1, vjust=0.5))
plot.AssIn.contiglength.unicycler
```

SPAdes contig number over 500bp

```{r}
# contig count
plot.AssIn.contignum.spades500 <- inputassemblyQuast$spades %>%
  filter(QuastType == 'ChromosomeAndPlasmid') %>%
  ggplot(aes(x=X..contigs)) +
  geom_histogram(binwidth = 10,fill='#fdb462') +
  theme_bw() +
  labs(
    x="Number of Contigs",
    y="Count",
    title = "SPAdes Assemblies - Number of Contigs, >500bp"
  ) +
  xlim(0,1000)
plot.AssIn.contignum.spades500
```

SPAdes all contig number

```{r}
plot.AssIn.contignum.spades <- inputassemblyQuast$spades %>%
  filter(QuastType == 'ChromosomeAndPlasmid') %>%
  ggplot(aes(x=X..contigs.....0.bp.)) +
  geom_histogram(binwidth = 10,fill='#fdb462') +
  theme_bw() +
  labs(
    x="Number of Contigs",
    y="Count",
    title = "SPAdes Assemblies - Number of Contigs"
  ) +
  xlim(0,4500)
plot.AssIn.contignum.spades
```

Unicycler contig number over 500bp

```{r}
plot.AssIn.contignum.unicycler500 <- inputassemblyQuast$unicycler %>%
  filter(QuastType == 'ChromosomeAndPlasmid') %>%
  ggplot(aes(x=X..contigs)) +
  geom_histogram(binwidth = 10,fill='#bebada') +
  theme_bw() +
  labs(
    x="Number of Contigs",
    y="Count",
    title = "Unicycler Assemblies - Number of Contigs, >500bp"
  ) +
  xlim(0,1000)
plot.AssIn.contignum.unicycler500
```

Unicycler all contigs histogram

```{r}
plot.AssIn.contignum.unicycler <- inputassemblyQuast$unicycler %>%
  filter(QuastType == 'ChromosomeAndPlasmid') %>%
  ggplot(aes(x=X..contigs.....0.bp.)) +
  geom_histogram(binwidth = 10,fill='#bebada') +
  theme_bw() +
  labs(
    x="Number of Contigs",
    y="Count",
    title = "Unicycler Assemblies - Number of Contigs"
  ) +
  xlim(0,4500)
plot.AssIn.contignum.unicycler
```

SPAdes auNGA 

```{r}
plot.AssIn.aunga.spades <- inputassemblyQuast$spades %>%
  filter(QuastType == 'ChromosomeAndPlasmid') %>%
  ggplot(aes(x=auNGA)) +
  geom_histogram(binwidth = 25000,fill='#fdb462') +
  theme_bw() +
  labs(
    x="auNGA",
    y="Count",
    title = "SPAdes Assemblies - auNGA"
  ) +
  xlim(0,2000000)
plot.AssIn.aunga.spades
```

Unicycler auNGA

```{r}
plot.AssIn.aunga.unicycler <- inputassemblyQuast$unicycler %>%
  filter(QuastType == 'ChromosomeAndPlasmid') %>%
  ggplot(aes(x=auNGA)) +
  geom_histogram(binwidth = 25000,fill='#bebada') +
  theme_bw() +
  labs(
    x="auNGA",
    y="Count",
    title = "Unicycler Assemblies - auNGA"
  ) +
  xlim(0,2000000)
plot.AssIn.aunga.unicycler
```

Multipanel plot

```{r}
ggarrange(
  plot.AssIn.contignum.spades,
  plot.AssIn.contignum.unicycler,
  plot.AssIn.contignum.spades500,
  plot.AssIn.contignum.unicycler500,
  plot.AssIn.contiglength.spades,
  plot.AssIn.contiglength.unicycler,
  plot.AssIn.aunga.spades,
  plot.AssIn.aunga.unicycler,
  nrow=4,ncol=2,
  labels = 'AUTO',
  align = 'hv'
)
#ggsave("Figures/SuppFigure2.pdf",dpi=300,units = 'cm',height = 35,width = 30)
```

## TPFPTNFN bars

Data from Table 2
True positive / negative and false positive / negative for SPAdes

```{r}
plot.tpfptnfn.bar.spades <- TPFPTNFN$spades %>%
  pivot_longer(-Tool) %>%
  separate_wider_delim(name,delim = ' - ',names = c("ToolPrediction","BlastResults"),too_few = 'align_start') %>%
  mutate(
    normValue = value / 117619,
    facetlabel = "Tool Prediction"
  ) %>%
  filter(ToolPrediction != 'total_rows') %>%
  ggplot(aes(y=normValue,x=Tool,fill=BlastResults)) +
  geom_col() +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45,hjust = 1)) +
  scale_fill_manual(values = c(
    "Chromosome Blast" = '#fc8d62',
    #"Mixed Blast" = "#8da0cb",
    "Plasmid Blast" = "#66c2a5"
  ), labels = c(
    "Chromosome Blast" = "Chromosome",
    #"Mixed Blast" = "Chromosome and Plasmid",
    "Plasmid Blast" = "Plasmid"
  )) +
  labs(
    y="Proportion of BLASTn Assigned Contigs (n=117,619)", 
    x='',
    fill='BLASTn Match',
    title="SPAdes Assembly Input"
  ) +
  #facet_nested(~ToolPrediction + BlastResults)
  facet_nested(~facetlabel + ToolPrediction,labeller=labeller(ToolPrediction=c("Chromosome Predicted" = "Chromosome", "No Classification" = "No Prediction", "Plasmid Predicted"="Plasmid")))
plot.tpfptnfn.bar.spades
```

Unicycler true positive / negative and false positive / negative

```{r}
plot.tpfptnfn.bar.unicycler <- TPFPTNFN$unicycler %>%
  pivot_longer(-Tool) %>%
  separate_wider_delim(name,delim = ' - ',names = c("ToolPrediction","BlastResults"),too_few = 'align_start') %>%
  mutate(
    normValue = value / 71224,
    facetlabel = "Tool Prediction"
  ) %>%
  filter(ToolPrediction != 'total_rows') %>%
  ggplot(aes(y=normValue,x=Tool,fill=BlastResults)) +
  geom_col() +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45,hjust = 1)) +
  scale_fill_manual(values = c(
    "Chromosome Blast" = '#fc8d62',
    #"Mixed Blast" = "#8da0cb",
    "Plasmid Blast" = "#66c2a5"
  ), labels = c(
    "Chromosome Blast" = "Chromosome",
    #"Mixed Blast" = "Chromosome and Plasmid",
    "Plasmid Blast" = "Plasmid"
  )) +
  labs(
    y="Proportion of BLASTn Assigned Contigs (n=71,224)", 
    x='',
    fill='BLASTn Match',
    title="Unicycler Assembly Input"
  ) +
  #facet_nested(~ToolPrediction + BlastResults)
  facet_nested(~facetlabel + ToolPrediction,labeller=labeller(ToolPrediction=c("Chromosome Predicted" = "Chromosome", "No Classification" = "No Prediction", "Plasmid Predicted"="Plasmid")))
plot.tpfptnfn.bar.unicycler
```

Multipanel

```{r}
ggarrange(
  plot.tpfptnfn.bar.spades,
  plot.tpfptnfn.bar.unicycler,
  nrow=2,ncol=1,
  labels = 'AUTO',
  align = 'hv'
)
#ggsave("Figures/SuppFigure3.pdf",dpi=300,units = 'cm',height=25,width=25)
```


## Unicycler Precision, Recall and F1

Numbers
Plasmidome precision - Unicycler
```{r}
quastMetricsTyping$unicycler %>%
  filter(QuastType == 'CombinedPlasmids') %>%
  group_by(ToolName) %>%
  summarise(
    med = median(Precision,na.rm = T),
    lq = quantile(Precision,0.25,na.rm = T),
    uq = quantile(Precision,0.75,na.rm = T),
    min = min(Precision,na.rm = T),
    max = max(Precision,na.rm = T)
  )
```

Plasmidome recall - Unicycler
```{r}
quastMetricsTyping$unicycler %>%
  filter(QuastType == 'CombinedPlasmids') %>%
  group_by(ToolName) %>%
  summarise(
    med = median(Recall,na.rm = T),
    lq = quantile(Recall,0.25,na.rm = T),
    uq = quantile(Recall,0.75,na.rm = T),
    min = min(Recall,na.rm = T),
    max = max(Recall,na.rm = T)
  )
```

Plasmidome F1 - Unicycler
```{r}
quastMetricsTyping$unicycler %>%
  filter(QuastType == 'CombinedPlasmids') %>%
  group_by(ToolName) %>%
  summarise(
    med = median(F1,na.rm = T),
    lq = quantile(F1,0.25,na.rm = T),
    uq = quantile(F1,0.75,na.rm = T),
    min = min(F1,na.rm = T),
    max = max(F1,na.rm = T)
  )
```

Plots

Plasmidome recall - Unicycler
Just plot tools that take assembly input
Set PlaScope (assembly) to 0 as it didn't make any predictions
```{r}
plot.quast.recall.uni <- quastMetricsTyping$unicycler %>%
  filter(QuastType == 'CombinedPlasmids', InputType == 'Assembly Based') %>% #isolate level
  add_row(ToolName = "PlaScope (assembly)",Recall=NA,InputType="Assembly Based") %>% #for adding PlaScope (assembly)
  ggplot(aes(x=ToolName,y=Recall,fill=ToolName,colour=ToolName)) +
  #geom_beeswarm() +
  #geom_violin()+
  geom_boxplot() +
  #scale_x_discrete(breaks=c("HyAsp","MOB-suite","PlaScope (assembly)","PLASMe","Plasmer","PlasmidHunter","Platon","PlaScope (reads)","plasmidSPAdes"),drop=F) +
  scale_fill_manual(values = plasmid.tool.colours.fill) +
  scale_color_manual(values= plasmid.tool.colours) +
  ylim(-0.05,1) +
  theme_bw() +
  theme(
    legend.position = 'None',
    axis.title.x = element_blank(),
        panel.grid.major.x = element_blank()
    ) +
  labs(y="Recall - Total Plasmid Content") +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))#+
  #facet_grid(cols = vars(InputType),scales = 'free_x',space='free_x')
plot.quast.recall.uni
#ggsave("Figures/ToolRecall.pdf",dpi = 300,units = 'cm',width=14,height = 8)
```

Plasmidome precision - Unicycler
```{r}
plot.quast.precision.uni <- quastMetricsTyping$unicycler %>%
  filter(QuastType == 'CombinedPlasmids', InputType == 'Assembly Based') %>% #isolate level
  add_row(ToolName = "PlaScope (assembly)",Recall=NA,InputType="Assembly Based") %>% #for adding PlaScope (assembly)
  ggplot(aes(x=ToolName,y=Precision,fill=ToolName,colour=ToolName)) +
  #geom_beeswarm() +
  #geom_violin()+
  geom_boxplot() +
  scale_fill_manual(values = plasmid.tool.colours.fill) +
  scale_color_manual(values = plasmid.tool.colours) +
  ylim(-0.05,1) +
  theme_bw() +
  theme(
    legend.position = 'None',
    axis.title.x = element_blank(),
        panel.grid.major.x = element_blank()
    ) +
  labs(y="Precision - Total Plasmid Content") +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))#+
  #facet_grid(cols = vars(InputType),scales = 'free_x',space='free_x')
plot.quast.precision.uni
#ggsave("Figures/ToolPrecision.pdf",dpi = 300,units = 'cm',width=14,height = 8)
```

Plasmidome F1 - Unicycler
```{r}
plot.quast.f1.uni <- quastMetricsTyping$unicycler %>%
  filter(QuastType == 'CombinedPlasmids', InputType == 'Assembly Based') %>% #isolate level
  add_row(ToolName = "PlaScope (assembly)",Recall=NA,InputType="Assembly Based") %>% #for adding PlaScope (assembly)
  ggplot(aes(x=ToolName,y=F1,fill=ToolName,colour = ToolName)) +
  #geom_beeswarm() +
  #geom_violin()+
  geom_boxplot() +
  scale_fill_manual(values = plasmid.tool.colours.fill) +
  scale_color_manual(values = plasmid.tool.colours) +
  ylim(-0.05,1) +
  theme_bw() +
  theme(
    legend.position = 'None',
    axis.title.x = element_blank(),
        panel.grid.major.x = element_blank()
    ) +
  labs(y="F1 - Total Plasmid Content") +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))#+
  #facet_grid(cols = vars(InputType),scales = 'free_x',space='free_x')
plot.quast.f1.uni
#ggsave("Figures/ToolF1.pdf",dpi = 300,units = 'cm',width=14,height = 8)
```

Multipanel
```{r}
plot.Supfig4.uni <-  ggarrange(
  plot.quast.precision.uni, #+ rremove('x.text') +rremove('x.ticks'),
  plot.quast.recall.uni, #+ rremove('x.text')+rremove('x.ticks'),
  plot.quast.f1.uni,
  nrow=3,
  align='hv',
  labels = 'AUTO'
)
#ggsave("Figures/SuppFigure4.pdf",dpi=300,units = 'cm',height = 25,width = 18)
plot.Supfig4.uni
```

## Duplication

Individual plasmid duplication metric against plasmid length

Read based tools
```{r}
breaks <- 10^(-10:10)
minor_breaks <- rep(1:9, 21)*(10^rep(-10:10, each=9))

plot.IndPlasLength.Dupe.reads <- quastMetricsTyping$spades %>%
  filter(QuastType == 'IndividualPlasmids',InputType == 'Read Based', Recall !=0) %>%
  mutate(
    Reference.length.kbp = Reference.length / 1000,
    FacetLabel = "Read Based Tools"
  ) %>%
  ggplot(aes(x=Reference.length.kbp,y=Duplication.ratio,colour = ToolName)) +
  geom_point(alpha=0.4) +
  scale_colour_manual(values = plasmid.tool.colours) +
  theme_bw() +
  labs(
    x = "Reference Plasmid Length (Kbp)",
    y = "Duplication Ratio - Individual Plasmids"
    ) +
  theme(
    legend.position = 'None'
    ) +
  #geom_vline(xintercept = 20)+
  scale_x_log10(breaks = breaks, minor_breaks=minor_breaks) +
  facet_nested(~FacetLabel + ToolName)
plot.IndPlasLength.Dupe.reads
```

SPAdes input
```{r}
breaks <- 10^(-10:10)
minor_breaks <- rep(1:9, 21)*(10^rep(-10:10, each=9))

plot.IndPlasLength.Dupe.spades <- quastMetricsTyping$spades %>%
  filter(QuastType == 'IndividualPlasmids',InputType == 'Assembly Based',Recall!=0) %>%
  mutate(
    Reference.length.kbp = Reference.length / 1000,
    FacetLabel = "SPAdes Assembly Input"
  ) %>%
  ggplot(aes(x=Reference.length.kbp,y=Duplication.ratio,colour = ToolName)) +
  geom_point(alpha=0.4) +
  scale_colour_manual(values = plasmid.tool.colours) +
  theme_bw() +
  labs(
    x = "Reference Plasmid Length (Kbp)",
    y = "Duplication Ratio - Individual Plasmids"
    ) +
  theme(
    legend.position = 'None'
    ) +
  #geom_vline(xintercept = 20)+
  scale_x_log10(breaks = breaks, minor_breaks=minor_breaks) +
  facet_nested(~FacetLabel + factor(ToolName,levels=c("HyAsp","MOB-suite","PLASMe","PlaScope (assembly)","Plasmer","PlasmidHunter","Platon")))
plot.IndPlasLength.Dupe.spades
```

Unicycler input
```{r}
breaks <- 10^(-10:10)
minor_breaks <- rep(1:9, 21)*(10^rep(-10:10, each=9))

plot.IndPlasLength.Dupe.unicycler <- quastMetricsTyping$unicycler %>%
  filter(QuastType == 'IndividualPlasmids',InputType == 'Assembly Based', Recall!=0) %>%
  add_row(ToolName = "PlaScope (assembly)",Duplication.ratio=NA,InputType="Assembly Based") %>% #for adding PlaScope (assembly)
  mutate(
    Reference.length.kbp = Reference.length / 1000,
    FacetLabel = "Unicycler Assembly Input"
  ) %>%
  ggplot(aes(x=Reference.length.kbp,y=Duplication.ratio,colour = ToolName)) +
  geom_point(alpha=0.4) +
  geom_text(
    data = data.frame(FacetLabel = "Unicycler Assembly Input", ToolName = "PlaScope (assembly)", label = "No\nPredictions"), 
    aes(label   = label),
    x=I(0.5), #middle of plot
    y=I(0.5),
    colour = "grey45",
    size = 4
  ) +
  scale_colour_manual(values = plasmid.tool.colours) +
  theme_bw() +
  labs(
    x = "Reference Plasmid Length (Kbp)",
    y = "Duplication Ratio - Individual Plasmids"
    ) +
  theme(
    legend.position = 'None'
    ) +
  #geom_vline(xintercept = 20)+
  scale_x_log10(breaks = breaks, minor_breaks=minor_breaks) +
  facet_nested(~FacetLabel + factor(ToolName,levels=c("HyAsp","MOB-suite","PLASMe","PlaScope (assembly)","Plasmer","PlasmidHunter","Platon")))
plot.IndPlasLength.Dupe.unicycler
```

Plot duplication ratio of the plasmids against the duplication ration of the input assemblies
Add x = y line

SPAdes input

```{r}
f <- function(x) x
breaks <- 10^(-10:10)
minor_breaks <- rep(1:9, 21)*(10^rep(-10:10, each=9))

plot.IndPlasDupe.Dupe.spades <- quastMetricsTyping$spades %>%
  filter(QuastType == 'IndividualPlasmids',InputType == 'Assembly Based', Recall!=0) %>%
  mutate(
    Reference.length.kbp = Reference.length / 1000,
    FacetLabel = "SPAdes Assembly Input"
  ) %>%
  ggplot(aes(x=InputDuplicationRatio,y=Duplication.ratio,colour = ToolName)) +
  geom_point(alpha=0.4) +
  scale_colour_manual(values = plasmid.tool.colours) +
  theme_bw() +
  labs(
    x = "Duplication Ratio - Input Assembly",
    y = "Duplication Ratio - Individual Plasmid Predictions"
    ) +
  theme(
    legend.position = 'None'
    ) +
  stat_function(fun=f,color='black') +
  #geom_vline(xintercept = 20)+
  #scale_x_log10(breaks = breaks, minor_breaks=minor_breaks) +
  facet_nested(~FacetLabel + factor(ToolName,levels=c("HyAsp","MOB-suite","PLASMe","PlaScope (assembly)","Plasmer","PlasmidHunter","Platon")))
plot.IndPlasDupe.Dupe.spades
```

Unicycler input

```{r}
f <- function(x) x
breaks <- 10^(-10:10)
minor_breaks <- rep(1:9, 21)*(10^rep(-10:10, each=9))

plot.IndPlasDupe.Dupe.unicycler <- quastMetricsTyping$unicycler %>%
  filter(QuastType == 'IndividualPlasmids',InputType == 'Assembly Based', Recall!=0) %>%
  add_row(ToolName = "PlaScope (assembly)",Duplication.ratio=NA,InputType="Assembly Based") %>% #for adding PlaScope (assembly)
  mutate(
    Reference.length.kbp = Reference.length / 1000,
    FacetLabel = "Unicycler Assembly Input"
  ) %>%
  ggplot(aes(x=InputDuplicationRatio,y=Duplication.ratio,colour = ToolName)) +
  geom_point(alpha=0.4) +
  geom_text(
    data = data.frame(FacetLabel = "Unicycler Assembly Input", ToolName = "PlaScope (assembly)", label = "No\nPredictions"), 
    aes(label   = label),
    x=I(0.5), #middle of plot
    y=I(0.5),
    colour = "grey45",
    size = 4
  ) +
  scale_colour_manual(values = plasmid.tool.colours) +
  theme_bw() +
  labs(
    x = "Duplication Ratio - Input Assembly",
    y = "Duplication Ratio - Individual Plasmid Predictions"
    ) +
  theme(
    legend.position = 'None'
    ) +
  stat_function(fun=f,color='black') +
  #geom_vline(xintercept = 20)+
  #scale_x_log10(breaks = breaks, minor_breaks=minor_breaks) +
  facet_nested(~FacetLabel + factor(ToolName,levels=c("HyAsp","MOB-suite","PLASMe","PlaScope (assembly)","Plasmer","PlasmidHunter","Platon")))
plot.IndPlasDupe.Dupe.unicycler
```

Multipanel duplication ratio against length
```{r}
ggarrange(
  plot.IndPlasLength.Dupe.spades,
  plot.IndPlasLength.Dupe.reads,
  plot.IndPlasLength.Dupe.unicycler,
  nrow=2,ncol=2,
  labels = c("A","C","B"),
  align = 'hv',
  widths = c(1,0.35)
)
#ggsave("Figures/SuppFigure5.pdf",dpi=300,units = 'cm',height = 17.5,width = 32.5)
```

Multipanel duplication of input and output
```{r}
ggarrange(
  plot.IndPlasDupe.Dupe.spades,
  plot.IndPlasDupe.Dupe.unicycler,
  nrow=2,ncol=1,
  labels = 'AUTO',
  align = 'hv'
)
#ggsave("Figures/SuppFigure6.pdf",dpi=300,units = 'cm',height = 20,width = 30)
```


## Plasmidome length against F1

Spearman's correlation test for association

```{r}
quastMetricsTyping$spades %>%
  filter(QuastType == 'CombinedPlasmids') %>%
  group_by(ToolName) %>%
  summarise(
    test = list(cor.test(F1,Reference.length,method='spearman') %>% tidy())
  ) %>%
  unnest(test)
```

SPAdes plot

```{r}
breaks <- 10^(-10:10)
minor_breaks <- rep(1:9, 21)*(10^rep(-10:10, each=9))

plot.AllPlasLength.F1.spades <- quastMetricsTyping$spades %>%
  filter(QuastType == 'CombinedPlasmids',InputType == 'Assembly Based') %>%
  mutate(
    Reference.length.kbp = Reference.length / 1000,
    FacetLabel = "SPAdes Assembly Input"
  ) %>%
  ggplot(aes(x=Reference.length.kbp,y=F1,colour = ToolName)) +
  geom_point(alpha=0.4) +
  scale_colour_manual(values = plasmid.tool.colours) +
  theme_bw() +
  labs(
    x = "Total Plasmid Length (Kbp) in Hybrid Genome",
    y = "F1 Score - Total Plasmid Content"
    ) +
  theme(
    legend.position = 'None'
    ) +
  #geom_vline(xintercept = 100,colour='grey')+
  scale_x_log10(breaks = breaks, minor_breaks=minor_breaks) +
  facet_nested(~FacetLabel + factor(ToolName,levels=c("HyAsp","MOB-suite","PLASMe","PlaScope (assembly)","Plasmer","PlasmidHunter","Platon")))
plot.AllPlasLength.F1.spades
```

Unicycler plot

```{r}
breaks <- 10^(-10:10)
minor_breaks <- rep(1:9, 21)*(10^rep(-10:10, each=9))

plot.AllPlasLength.F1.unicycler <- quastMetricsTyping$unicycler %>%
  filter(QuastType == 'CombinedPlasmids',InputType == 'Assembly Based') %>%
  add_row(ToolName = "PlaScope (assembly)",F1=NA,InputType="Assembly Based") %>% #for adding PlaScope (assembly)
  mutate(
    Reference.length.kbp = Reference.length / 1000,
    FacetLabel = "Unicycler Assembly Input"
  ) %>%
  ggplot(aes(x=Reference.length.kbp,y=F1,colour = ToolName)) +
  geom_point(alpha=0.4) +
  geom_text(
    data = data.frame(FacetLabel = "Unicycler Assembly Input", ToolName = "PlaScope (assembly)", label = "No\nPredictions"), 
    aes(label   = label),
    x=I(0.5), #middle of plot
    y=I(0.5),
    colour = "grey45",
    size = 4
  ) +
  scale_colour_manual(values = plasmid.tool.colours) +
  theme_bw() +
  labs(
    x = "Total Plasmid Length (Kbp) in Hybrid Genome",
    y = "F1 Score - Total Plasmid Content"
    ) +
  theme(
    legend.position = 'None'
    ) +
  #geom_vline(xintercept = 20)+
  scale_x_log10(breaks = breaks, minor_breaks=minor_breaks) +
  facet_nested(~FacetLabel + factor(ToolName,levels=c("HyAsp","MOB-suite","PLASMe","PlaScope (assembly)","Plasmer","PlasmidHunter","Platon")))
plot.AllPlasLength.F1.unicycler
```

Read tool plot

```{r}
breaks <- 10^(-10:10)
minor_breaks <- rep(1:9, 21)*(10^rep(-10:10, each=9))

plot.AllPlasLength.F1.reads <- quastMetricsTyping$unicycler %>%
  filter(QuastType == 'CombinedPlasmids',InputType == 'Read Based') %>%
  mutate(
    Reference.length.kbp = Reference.length / 1000,
    FacetLabel = "Read Based Tools"
  ) %>%
  ggplot(aes(x=Reference.length.kbp,y=F1,colour = ToolName)) +
  geom_point(alpha=0.4) +
  scale_colour_manual(values = plasmid.tool.colours) +
  theme_bw() +
  labs(
    x = "Total Plasmid Length (Kbp) in Hybrid Genome",
    y = "F1 Score - Total Plasmid Content"
    ) +
  theme(
    legend.position = 'None'
    ) +
  #geom_vline(xintercept = 20)+
  scale_x_log10(breaks = breaks, minor_breaks=minor_breaks) +
  facet_nested(~FacetLabel + ToolName)
plot.AllPlasLength.F1.reads
```


Multipanel
```{r}
ggarrange(
  plot.AllPlasLength.F1.spades,
  plot.AllPlasLength.F1.reads,
  plot.AllPlasLength.F1.unicycler,
  nrow=2,ncol=2,
  labels = c("A","C","B"),
  align = 'hv',
  widths = c(1,0.35)
)
#ggsave("Figures/SuppFigure7.pdf",dpi=300,units = 'cm',height = 17.5,width = 32.5)
```


## Individual plasmid length

Spearman's test for correlation

```{r}
quastMetricsTyping$spades %>%
  filter(QuastType == 'IndividualPlasmids') %>%
  group_by(ToolName) %>%
  summarise(
    test = list(cor.test(Recall,Reference.length,method='spearman') %>% tidy())
  ) %>%
  unnest(test)
```

Read tool plot

```{r}
breaks <- 10^(-10:10)
minor_breaks <- rep(1:9, 21)*(10^rep(-10:10, each=9))

plot.IndPlasLength.Recall.reads <- quastMetricsTyping$unicycler %>%
  filter(QuastType == 'IndividualPlasmids',InputType == 'Read Based') %>%
  mutate(
    Reference.length.kbp = Reference.length / 1000,
    FacetLabel = "Read Based Tools"
  ) %>%
  ggplot(aes(x=Reference.length.kbp,y=Recall,colour = ToolName)) +
  geom_point(alpha=0.4) +
  scale_colour_manual(values = plasmid.tool.colours) +
  theme_bw() +
  labs(
    x = "Individual Plasmid Length (Kbp) in Hybrid Genome",
    y = "Recall Score for Individual Plasmids"
    ) +
  theme(
    legend.position = 'None'
    ) +
  #geom_vline(xintercept = 20)+
  scale_x_log10(breaks = breaks, minor_breaks=minor_breaks) +
  facet_nested(~FacetLabel + ToolName)
plot.IndPlasLength.Recall.reads
```

SPAdes plot

```{r}
breaks <- 10^(-10:10)
minor_breaks <- rep(1:9, 21)*(10^rep(-10:10, each=9))

plot.IndPlasLength.Recall.spades <- quastMetricsTyping$spades %>%
  filter(QuastType == 'IndividualPlasmids',InputType == 'Assembly Based') %>%
  add_row(ToolName = "PlaScope (assembly)",Recall=NA,InputType="Assembly Based") %>% #for adding PlaScope (assembly)
  mutate(
    Reference.length.kbp = Reference.length / 1000,
    FacetLabel = "SPAdes Assembly Input"
  ) %>%
  ggplot(aes(x=Reference.length.kbp,y=Recall,colour = ToolName)) +
  geom_point(alpha=0.4) +
  scale_colour_manual(values = plasmid.tool.colours) +
  theme_bw() +
  labs(
    x = "Individual Plasmid Length (Kbp) in Hybrid Genome",
    y = "Recall Score for Individual Plasmids"
    ) +
  theme(
    legend.position = 'None'
    ) +
  #geom_vline(xintercept = 20)+
  scale_x_log10(breaks = breaks, minor_breaks=minor_breaks) +
  facet_nested(~FacetLabel + factor(ToolName,levels=c("HyAsp","MOB-suite","PLASMe","PlaScope (assembly)","Plasmer","PlasmidHunter","Platon")))
plot.IndPlasLength.Recall.spades
```

Get numbers of plasmids less than 20kbp with recall less than 0.05

```{r}
quastMetricsTyping$spades %>%
  filter(QuastType == 'IndividualPlasmids', ToolName %in% c("MOB-suite","PlaScope (assembly)","PlaScope (reads)"), Reference.length < 20000) %>%
  mutate(
    RecallCat = cut(Recall, breaks=c(-1,0.05,0.95,1), labels=c("Less than 0.05","Between","Above 0.95"))
  ) %>%
  group_by(ToolName) %>%
  count(RecallCat) %>%
  pivot_wider(names_from = RecallCat, values_from = n)
```

Unicycler plot

```{r}
breaks <- 10^(-10:10)
minor_breaks <- rep(1:9, 21)*(10^rep(-10:10, each=9))

plot.IndPlasLength.Recall.unicycler <- quastMetricsTyping$unicycler %>%
  filter(QuastType == 'IndividualPlasmids',InputType == 'Assembly Based') %>%
  add_row(ToolName = "PlaScope (assembly)",Recall=NA,InputType="Assembly Based") %>% #for adding PlaScope (assembly)
  mutate(
    Reference.length.kbp = Reference.length / 1000,
    FacetLabel = "Unicycler Assembly Input"
  ) %>%
  ggplot(aes(x=Reference.length.kbp,y=Recall,colour = ToolName)) +
  geom_point(alpha=0.4) +
  geom_text(
    data = data.frame(FacetLabel = "Unicycler Assembly Input", ToolName = "PlaScope (assembly)", label = "No\nPredictions"), 
    aes(label   = label),
    x=I(0.5), #middle of plot
    y=I(0.5),
    colour = "grey45",
    size = 4
  ) +
  scale_colour_manual(values = plasmid.tool.colours) +
  theme_bw() +
  labs(
    x = "Individual Plasmid Length (Kbp) in Hybrid Genome",
    y = "Recall Score for Individual Plasmids"
    ) +
  theme(
    legend.position = 'None'
    ) +
  #geom_vline(xintercept = 20)+
  scale_x_log10(breaks = breaks, minor_breaks=minor_breaks) +
  facet_nested(~FacetLabel + factor(ToolName,levels=c("HyAsp","MOB-suite","PLASMe","PlaScope (assembly)","Plasmer","PlasmidHunter","Platon")))
plot.IndPlasLength.Recall.unicycler
```

Multipanel

```{r}
ggarrange(
  plot.IndPlasLength.Recall.spades,
  plot.IndPlasLength.Recall.reads,
  plot.IndPlasLength.Recall.unicycler,
  nrow=2,ncol=2,
  labels = c("A","C","B"),
  align = 'hv',
  widths = c(1,0.35)
)
#ggsave("Figures/SuppFigure8.pdf",dpi=300,units = 'cm',height = 17.5,width = 32.5)
```


## Total resistance against F1

Spearman's correlation test

```{r}
quastMetricsTyping$spades %>%
  filter(QuastType == 'CombinedPlasmids') %>%
  group_by(ToolName) %>%
  summarise(
    test = list(cor.test(F1,AMRcount,method='spearman') %>% tidy())
  ) %>%
  unnest(test)
```

Read based tools

```{r}
plot.AllPlasAMR.F1.reads <-quastMetricsTyping$spades %>%
  filter(QuastType == 'CombinedPlasmids',InputType=='Read Based') %>%
  mutate(FacetLabel = "Read Based Tools") %>%
  ggplot(aes(x=AMRcount,y=F1,colour = ToolName)) +
  geom_point(alpha=0.4) +
  scale_colour_manual(values = plasmid.tool.colours) +
  theme_bw() +
  theme(legend.position = 'none') +
  labs(
    x = "Resistance Gene Count on All Plasmids in Isolate",
    y = "F1 - Total Plasmid Content"
  ) +
  facet_nested(~FacetLabel + ToolName)
plot.AllPlasAMR.F1.reads
```

SPAdes plot

```{r}
plot.AllPlasAMR.F1.spades <- quastMetricsTyping$spades %>%
  filter(QuastType == 'CombinedPlasmids',InputType=='Assembly Based') %>%
  mutate(FacetLabel = "SPAdes Assembly Input") %>%
  ggplot(aes(x=AMRcount,y=F1,colour = ToolName)) +
  geom_point(alpha=0.4) +
  scale_colour_manual(values = plasmid.tool.colours) +
  theme_bw() +
  theme(legend.position = 'none') +
  labs(
    x = "Resistance Gene Count on All Plasmids in Isolate",
    y = "F1 - Total Plasmid Content"
  ) +
  facet_nested(~FacetLabel + factor(ToolName,levels=c("HyAsp","MOB-suite","PLASMe","PlaScope (assembly)","Plasmer","PlasmidHunter","Platon")))
plot.AllPlasAMR.F1.spades
```

Unicycler plot

```{r}
plot.AllPlasAMR.F1.unicycler <- quastMetricsTyping$unicycler %>%
  filter(QuastType == 'CombinedPlasmids',InputType=='Assembly Based',ToolName != 'PlaScope (assembly)') %>% #filter out plascope: no predictions
  add_row(ToolName = "PlaScope (assembly)",F1=NA,InputType="Assembly Based") %>% #for adding PlaScope (assembly)
  mutate(FacetLabel = "Unicycler Assembly Input") %>%
  ggplot(aes(x=AMRcount,y=F1,colour = ToolName)) +
  geom_point(alpha=0.4) +
  geom_text(
    data = data.frame(FacetLabel = "Unicycler Assembly Input", ToolName = "PlaScope (assembly)", label = "No\nPredictions"), 
    aes(label   = label),
    x=I(0.5), #middle of plot
    y=I(0.5),
    colour = "grey45",
    size = 4
  ) +
  scale_colour_manual(values = plasmid.tool.colours) +
  theme_bw() +
  theme(legend.position = 'none') +
  labs(
    x = "Resistance Gene Count on All Plasmids in Isolate",
    y = "F1 - Total Plasmid Content"
  ) +
  facet_nested(~FacetLabel + factor(ToolName,levels=c("HyAsp","MOB-suite","PLASMe","PlaScope (assembly)","Plasmer","PlasmidHunter","Platon")))
plot.AllPlasAMR.F1.unicycler
```
Multipanel

```{r}
ggarrange(
  plot.AllPlasAMR.F1.spades,
  plot.AllPlasAMR.F1.reads,
  plot.AllPlasAMR.F1.unicycler,
  nrow=2,ncol=2,
  labels = c("A","C","B"),
  align = 'hv',
  widths = c(1,0.35)
)
#ggsave("Figures/SuppFigure9.pdf",dpi=300,units = 'cm',height = 17.5,width = 32.5)
```

## Ind. Plasmid Resistance against recall

Correlation test

```{r}
quastMetricsTyping$spades %>%
  filter(QuastType == 'IndividualPlasmids') %>%
  group_by(ToolName) %>%
  summarise(
    test = list(cor.test(Recall,AMRcount,method='spearman') %>% tidy())
  ) %>%
  unnest(test)
```

Read based tools plot

```{r}
plot.IndPlasAMR.Recall.reads <-quastMetricsTyping$spades %>%
  filter(QuastType == 'IndividualPlasmids',InputType=='Read Based') %>%
  mutate(FacetLabel = "Read Based Tools") %>%
  ggplot(aes(x=AMRcount,y=Recall,colour = ToolName)) +
  geom_point(alpha=0.4) +
  scale_colour_manual(values = plasmid.tool.colours) +
  theme_bw() +
  theme(legend.position = 'none') +
  labs(
    x = "Resistance Gene Count on\nIndividual Plasmids in Isolate",
    y = "Recall - Individual Plasmids"
  ) +
  facet_nested(~FacetLabel + ToolName)
plot.IndPlasAMR.Recall.reads
```

SPAdes plot

```{r}
plot.IndPlasAMR.Recall.spades <- quastMetricsTyping$spades %>%
  filter(QuastType == 'IndividualPlasmids',InputType=='Assembly Based') %>%
  mutate(FacetLabel = "SPAdes Assembly Input") %>%
  ggplot(aes(x=AMRcount,y=Recall,colour = ToolName)) +
  geom_point(alpha=0.4) +
  scale_colour_manual(values = plasmid.tool.colours) +
  theme_bw() +
  theme(legend.position = 'none') +
  labs(
    x = "Resistance Gene Count on Individual Plasmids in Isolate",
    y = "Recall - Individual Plasmids"
  ) +
  facet_nested(~FacetLabel + factor(ToolName,levels=c("HyAsp","MOB-suite","PLASMe","PlaScope (assembly)","Plasmer","PlasmidHunter","Platon")))
plot.IndPlasAMR.Recall.spades
```

Unicycler plot

```{r}
plot.IndPlasAMR.Recall.unicycler <- quastMetricsTyping$unicycler %>%
  filter(QuastType == 'IndividualPlasmids',InputType=='Assembly Based') %>%
  add_row(ToolName = "PlaScope (assembly)",Recall=NA,InputType="Assembly Based") %>% #for adding PlaScope (assembly)
  mutate(FacetLabel = "Unicycler Assembly Input") %>%
  ggplot(aes(x=AMRcount,y=Recall,colour = ToolName)) +
  geom_point(alpha=0.4) +
  geom_text(
    data = data.frame(FacetLabel = "Unicycler Assembly Input", ToolName = "PlaScope (assembly)", label = "No\nPredictions"), 
    aes(label   = label),
    x=I(0.5), #middle of plot
    y=I(0.5),
    colour = "grey45",
    size = 4
  ) +
  scale_colour_manual(values = plasmid.tool.colours) +
  theme_bw() +
  theme(legend.position = 'none') +
  labs(
    x = "Resistance Gene Count on Individual Plasmids in Isolate",
    y = "Recall - Individual Plasmids"
  ) +
  facet_nested(~FacetLabel + factor(ToolName,levels=c("HyAsp","MOB-suite","PLASMe","PlaScope (assembly)","Plasmer","PlasmidHunter","Platon")))
plot.IndPlasAMR.Recall.unicycler
```

Multipanel

```{r}
ggarrange(
  plot.IndPlasAMR.Recall.spades,
  plot.IndPlasAMR.Recall.reads,
  plot.IndPlasAMR.Recall.unicycler,
  nrow=2,ncol=2,
  labels = c("A","C","B"),
  align = 'hv',
  widths = c(1,0.35)
)
#ggsave("Figures/SuppFigure10.pdf",dpi=300,units = 'cm',height = 17.5,width = 32.5)
```


## IS element

Correlation test

```{r}
quastMetricsTyping$spades %>%
  filter(QuastType == 'IndividualPlasmids') %>%
  group_by(ToolName) %>%
  summarise(
    test = list(cor.test(Recall,num_element_IS,method='spearman') %>% tidy())
  ) %>%
  unnest(test)
```

Read based tools plot

```{r}
plot.IndPlasIS.Recall.reads <-quastMetricsTyping$spades %>%
  filter(QuastType == 'IndividualPlasmids',InputType=='Read Based') %>%
  mutate(FacetLabel = "Read Based Tools") %>%
  ggplot(aes(x=num_element_IS,y=Recall,colour = ToolName)) +
  geom_point(alpha=0.4) +
  scale_colour_manual(values = plasmid.tool.colours) +
  theme_bw() +
  theme(legend.position = 'none') +
  labs(
    x = "IS Elements on\nIndividual Plasmids in Isolate",
    y = "Recall - Individual Plasmids"
  ) +
  facet_nested(~FacetLabel + ToolName)
plot.IndPlasIS.Recall.reads
```

SPAdes plot

```{r}
plot.IndPlasIS.Recall.spades <- quastMetricsTyping$spades %>%
  filter(QuastType == 'IndividualPlasmids',InputType=='Assembly Based') %>%
  mutate(FacetLabel = "SPAdes Assembly Input") %>%
  ggplot(aes(x=num_element_IS,y=Recall,colour = ToolName)) +
  geom_point(alpha=0.4) +
  scale_colour_manual(values = plasmid.tool.colours) +
  theme_bw() +
  theme(legend.position = 'none') +
  labs(
    x = "IS Elements on Individual Plasmids in Isolate",
    y = "Recall - Individual Plasmids"
  ) +
  facet_nested(~FacetLabel + factor(ToolName,levels=c("HyAsp","MOB-suite","PLASMe","PlaScope (assembly)","Plasmer","PlasmidHunter","Platon")))
plot.IndPlasIS.Recall.spades
```

Get numbers of plasmids with low IS count but low recall

```{r}
quastMetricsTyping$spades %>%
  filter(QuastType == 'IndividualPlasmids',num_element_IS<30,ToolName %in% c("MOB-suite","PlaScope (assembly)","PlaScope (reads)")) %>%
  mutate(
    RecallCat = cut(Recall, breaks=c(-1,0.95,1), labels=c("Less than 0.95","Above 0.95"))
  ) %>%
  group_by(ToolName) %>%
  count(RecallCat) %>%
  pivot_wider(names_from = RecallCat, values_from = n)
```

Unicycler plot

```{r}
plot.IndPlasIS.Recall.unicycler <- quastMetricsTyping$unicycler %>%
  filter(QuastType == 'IndividualPlasmids',InputType=='Assembly Based') %>%
  add_row(ToolName = "PlaScope (assembly)",Recall=NA,InputType="Assembly Based") %>% #for adding PlaScope (assembly)
  mutate(FacetLabel = "Unicycler Assembly Input") %>%
  ggplot(aes(x=num_element_IS,y=Recall,colour = ToolName)) +
  geom_point(alpha=0.4) +
  geom_text(
    data = data.frame(FacetLabel = "Unicycler Assembly Input", ToolName = "PlaScope (assembly)", label = "No\nPredictions"), 
    aes(label   = label),
    x=I(0.5), #middle of plot
    y=I(0.5),
    colour = "grey45",
    size = 4
  ) +
  scale_colour_manual(values = plasmid.tool.colours) +
  theme_bw() +
  theme(legend.position = 'none') +
  labs(
    x = "IS Elements on Individual Plasmids in Isolate",
    y = "Recall - Individual Plasmids"
  ) +
  facet_nested(~FacetLabel + factor(ToolName,levels=c("HyAsp","MOB-suite","PLASMe","PlaScope (assembly)","Plasmer","PlasmidHunter","Platon")))
plot.IndPlasIS.Recall.unicycler
```

Multipanel

```{r}
ggarrange(
  plot.IndPlasIS.Recall.spades,
  plot.IndPlasIS.Recall.reads,
  plot.IndPlasIS.Recall.unicycler,
  nrow=2,ncol=2,
  labels = c("A","C","B"),
  align = 'hv',
  widths = c(1,0.35)
)
#ggsave("Figures/SuppFigure11.pdf",dpi=300,units = 'cm',height = 17.5,width = 32.5)
```

Get maximum recall value achieved for plasmids with more than 30 IS elements
SPAdes

```{r}
quastMetricsTyping$spades %>%
  filter(QuastType == 'IndividualPlasmids',InputType=='Assembly Based',num_element_IS > 30,ToolName=='MOB-suite') %>%
  summarise(max(Recall))
```

Unicycler
```{r}
quastMetricsTyping$unicycler %>%
  filter(QuastType == 'IndividualPlasmids',InputType=='Assembly Based',num_element_IS > 30,ToolName=='MOB-suite') %>%
  summarise(max(Recall))
```

## Shared K-mers

Total plasmidome and Kmer sharing

Spearman's correlation test

```{r}
quastMetricsTyping$spades %>%
  filter(QuastType == 'CombinedPlasmids') %>%
  group_by(ToolName) %>%
  summarise(
    test = list(cor.test(F1,`MashSharedHashes(/100000)`,method='spearman') %>% tidy())
  ) %>%
  unnest(test)
```

Read based tools

```{r}
breaks <- 10^(-10:10)
minor_breaks <- rep(1:9, 21)*(10^rep(-10:10, each=9))

plot.AllPlasKmer.F1.reads <-quastMetricsTyping$spades %>%
  filter(QuastType == 'CombinedPlasmids',InputType=='Read Based') %>%
  mutate(FacetLabel = "Read Based Tools") %>%
  ggplot(aes(x=`MashSharedHashes(/100000)`,y=F1,colour = ToolName)) +
  geom_point(alpha=0.4) +
  scale_colour_manual(values = plasmid.tool.colours) +
  theme_bw() +
  theme(legend.position = 'none') +
  labs(
    x = "Shared Kmers between\nPlasmidome and Chromosome",
    y = "F1 - Total Plasmids"
  ) +
    scale_x_log10(breaks = breaks, minor_breaks = minor_breaks) +
  facet_nested(~FacetLabel + ToolName)
plot.AllPlasKmer.F1.reads
```

SPAdes plot

```{r}
plot.AllPlasKmer.F1.spades <- quastMetricsTyping$spades %>%
  filter(QuastType == 'CombinedPlasmids',InputType=='Assembly Based') %>%
  mutate(FacetLabel = "SPAdes Assembly Input") %>%
  ggplot(aes(x=`MashSharedHashes(/100000)`,y=F1,colour = ToolName)) +
  geom_point(alpha=0.4) +
  scale_colour_manual(values = plasmid.tool.colours) +
  theme_bw() +
  theme(legend.position = 'none') +
  labs(
    x = "Shared Kmers between Plasmidome and Chromosome",
    y = "F1 - Total Plasmids"
  ) +
  scale_x_log10(breaks = breaks, minor_breaks = minor_breaks) +
  facet_nested(~FacetLabel + factor(ToolName,levels=c("HyAsp","MOB-suite","PLASMe","PlaScope (assembly)","Plasmer","PlasmidHunter","Platon")))
plot.AllPlasKmer.F1.spades
```

Recall numbers of plasmids with low kmer sharing
```{r}
quastMetricsTyping$spades %>%
  filter(QuastType == 'IndividualPlasmids',`MashSharedHashes(/100000)`<200,ToolName %in% c("MOB-suite","PlaScope (assembly)","PlaScope (reads)")) %>%
  mutate(
    RecallCat = cut(Recall, breaks=c(-1,0.95,1), labels=c("Less than 0.95","Above 0.95"))
  ) %>%
  group_by(ToolName) %>%
  count(RecallCat) %>%
  pivot_wider(names_from = RecallCat, values_from = n)
```

Unicycler plot

```{r}
plot.AllPlasKmer.F1.unicycler <- quastMetricsTyping$unicycler %>%
  filter(QuastType == 'CombinedPlasmids',InputType=='Assembly Based', ToolName != 'PlaScope (assembly)') %>% #no plascope predictions
  add_row(ToolName = "PlaScope (assembly)",F1=NA,InputType="Assembly Based") %>% #for adding PlaScope (assembly)
  mutate(FacetLabel = "Unicycler Assembly Input") %>%
  ggplot(aes(x=`MashSharedHashes(/100000)`,y=F1,colour = ToolName)) +
  geom_point(alpha=0.4) +
  geom_text(
    data = data.frame(FacetLabel = "Unicycler Assembly Input", ToolName = "PlaScope (assembly)", label = "No\nPredictions"), 
    aes(label   = label),
    x=I(0.5), #middle of plot
    y=I(0.5),
    colour = "grey45",
    size = 4
  ) +
  scale_colour_manual(values = plasmid.tool.colours) +
  theme_bw() +
  theme(legend.position = 'none') +
  labs(
    x = "Shared Kmers between Plasmidome and Chromosome",
    y = "F1 - Total Plasmids"
  ) +
  scale_x_log10(breaks = breaks, minor_breaks = minor_breaks) +
  facet_nested(~FacetLabel + factor(ToolName,levels=c("HyAsp","MOB-suite","PLASMe","PlaScope (assembly)","Plasmer","PlasmidHunter","Platon")))
plot.AllPlasKmer.F1.unicycler
```

Multipanel

```{r}
ggarrange(
  plot.AllPlasKmer.F1.spades,
  plot.AllPlasKmer.F1.reads,
  plot.AllPlasKmer.F1.unicycler,
  nrow=2,ncol=2,
  labels = c("A","C","B"),
  align = 'hv',
  widths = c(1,0.35)
)
#ggsave("Figures/SuppFigure12.pdf",dpi=300,units = 'cm',height = 17.5,width = 32.5)
```


Individual plasmids Kmer sharing

Correlation test

```{r}
quastMetricsTyping$spades %>%
  filter(QuastType == 'IndividualPlasmids') %>%
  group_by(ToolName) %>%
  summarise(
    test = list(cor.test(Recall,`MashSharedHashes(/100000)`,method='spearman') %>% tidy())
  ) %>%
  unnest(test)
```

Read tool plot

```{r}
breaks <- 10^(-10:10)
minor_breaks <- rep(1:9, 21)*(10^rep(-10:10, each=9))

plot.IndPlasKmer.Recall.reads <-quastMetricsTyping$spades %>%
  filter(QuastType == 'IndividualPlasmids',InputType=='Read Based') %>%
  mutate(FacetLabel = "Read Based Tools") %>%
  ggplot(aes(x=`MashSharedHashes(/100000)`,y=Recall,colour = ToolName)) +
  geom_point(alpha=0.4) +
  scale_colour_manual(values = plasmid.tool.colours) +
  theme_bw() +
  theme(legend.position = 'none') +
  labs(
    x = "Kmers Shared Between Individual\nPlasmids and Chromosome in Isolate",
    y = "Recall - Individual Plasmids"
  ) +
    scale_x_log10(breaks = breaks, minor_breaks = minor_breaks) +
  facet_nested(~FacetLabel + ToolName)
plot.IndPlasKmer.Recall.reads
```

SPAdes plot

```{r}
breaks <- 10^(-10:10)
minor_breaks <- rep(1:9, 21)*(10^rep(-10:10, each=9))

plot.IndPlasKmer.Recall.spades <- quastMetricsTyping$spades %>%
  filter(QuastType == 'IndividualPlasmids',InputType=='Assembly Based') %>%
  mutate(FacetLabel = "SPAdes Assembly Input") %>%
  ggplot(aes(x=`MashSharedHashes(/100000)`,y=Recall,colour = ToolName)) +
  geom_point(alpha=0.4) +
  scale_colour_manual(values = plasmid.tool.colours) +
  theme_bw() +
  theme(legend.position = 'none') +
  labs(
    x = "Kmers Shared Between Individual Plasmids and Chromosome in Isolate",
    y = "Recall - Individual Plasmids"
  ) +
    scale_x_log10(breaks = breaks, minor_breaks = minor_breaks) +
  #geom_vline(xintercept = 250) +
  facet_nested(~FacetLabel + factor(ToolName,levels=c("HyAsp","MOB-suite","PLASMe","PlaScope (assembly)","Plasmer","PlasmidHunter","Platon")))
plot.IndPlasKmer.Recall.spades
```

Unicycler plot

```{r}
breaks <- 10^(-10:10)
minor_breaks <- rep(1:9, 21)*(10^rep(-10:10, each=9))

plot.IndPlasKmer.Recall.unicycler <- quastMetricsTyping$unicycler %>%
  filter(QuastType == 'IndividualPlasmids',InputType=='Assembly Based') %>%
  add_row(ToolName = "PlaScope (assembly)",Recall=NA,InputType="Assembly Based") %>% #for adding PlaScope (assembly)
  mutate(FacetLabel = "Unicycler Assembly Input") %>%
  ggplot(aes(x=`MashSharedHashes(/100000)`,y=Recall,colour = ToolName)) +
  geom_point(alpha=0.4) +
  geom_text(
    data = data.frame(FacetLabel = "Unicycler Assembly Input", ToolName = "PlaScope (assembly)", label = "No\nPredictions"), 
    aes(label   = label),
    x=I(0.5), #middle of plot
    y=I(0.5),
    colour = "grey45",
    size = 4
  ) +
  scale_colour_manual(values = plasmid.tool.colours) +
  theme_bw() +
  theme(legend.position = 'none') +
  labs(
    x = "Kmers Shared Between Individual Plasmids and Chromosome in Isolate",
    y = "Recall - Individual Plasmids"
  ) +
  scale_x_log10(breaks = breaks, minor_breaks = minor_breaks) +
  facet_nested(~FacetLabel + factor(ToolName,levels=c("HyAsp","MOB-suite","PLASMe","PlaScope (assembly)","Plasmer","PlasmidHunter","Platon")))
plot.IndPlasKmer.Recall.unicycler
```

Multipanel

```{r}
ggarrange(
  plot.IndPlasKmer.Recall.spades,
  plot.IndPlasKmer.Recall.reads,
  plot.IndPlasKmer.Recall.unicycler,
  nrow=2,ncol=2,
  labels = c("A","C","B"),
  align = 'hv',
  widths = c(1,0.35)
)
#ggsave("Figures/SuppFigure13.pdf",dpi=300,units = 'cm',height = 17.5,width = 32.5)
```


## coverage - just read based tools

Correlation test

```{r}
quastMetricsTyping$spades %>%
  filter(QuastType == 'IndividualPlasmids', InputType == 'Read Based') %>%
  group_by(ToolName) %>%
  summarise(
    test = list(cor.test(Recall,meandepthNorm,method='spearman') %>% tidy())
  ) %>%
  unnest(test)
```

Read tool plot
Add lines at normalised coverage of 1 and 2
1 = same depth as chromosome
```{r}
breaks <- 10^(-10:10)
minor_breaks <- rep(1:9, 21)*(10^rep(-10:10, each=9))

plot.IndPlasCov.Recall.reads <-quastMetricsTyping$spades %>%
  filter(QuastType == 'IndividualPlasmids',InputType=='Read Based') %>%
  mutate(FacetLabel = "Read Based Tools") %>%
  ggplot(aes(x=meandepthNorm,y=Recall,colour = ToolName)) +
  geom_point(alpha=0.4) +
  scale_colour_manual(values = plasmid.tool.colours) +
  theme_bw() +
  theme(legend.position = 'none') +
  labs(
    x = "Mean Sequencing Depth Normalised to Chromosome Depth",
    y = "Recall - Individual Plasmids"
  ) +
    scale_x_sqrt() +
  geom_vline(xintercept = 1) +
  geom_vline(xintercept = 2)+
  facet_nested(~FacetLabel + ToolName)
plot.IndPlasCov.Recall.reads

#ggsave("Figures/SuppFigure14.pdf",dpi=300,units = 'cm',height = 12.5,width = 15)
```


## Input assembly quality and deadends against performance

Contigs

Correlation test
```{r}
quastMetricsTyping$spades %>%
  filter(QuastType == 'CombinedPlasmids', InputType == 'Assembly Based') %>%
  group_by(ToolName) %>%
  summarise(
    test = list(cor.test(F1,InputContigCount,method='spearman') %>% tidy())
  ) %>%
  unnest(test)
```

SPAdes plot

```{r}
breaks <- 10^(-10:10)
minor_breaks <- rep(1:9, 21)*(10^rep(-10:10, each=9))

plot.AllPlasContigCount.F1.spades <- quastMetricsTyping$spades %>%
  filter(QuastType == 'CombinedPlasmids',InputType=='Assembly Based') %>%
  mutate(FacetLabel = "SPAdes Assembly Input") %>%
  ggplot(aes(x=InputContigCount,y=F1,colour = ToolName)) +
  geom_point(alpha=0.4) +
  scale_colour_manual(values = plasmid.tool.colours) +
  theme_bw() +
  theme(legend.position = 'none') +
  labs(
    x = "Number of Contigs in Input Assembly",
    y = "F1 - Total Plasmid Content"
  ) +
  scale_x_log10(breaks = breaks, minor_breaks = minor_breaks) +
  facet_nested(~FacetLabel + factor(ToolName,levels=c("HyAsp","MOB-suite","PLASMe","PlaScope (assembly)","Plasmer","PlasmidHunter","Platon")))
plot.AllPlasContigCount.F1.spades
```

Unicycler plot

```{r}
breaks <- 10^(-10:10)
minor_breaks <- rep(1:9, 21)*(10^rep(-10:10, each=9))

plot.AllPlasContigCount.F1.unicycler <- quastMetricsTyping$unicycler %>%
  filter(QuastType == 'CombinedPlasmids',InputType=='Assembly Based',ToolName!='PlaScope (assembly)') %>% #no plascope predictions
  add_row(ToolName = "PlaScope (assembly)",F1=NA,InputType="Assembly Based") %>% #for adding PlaScope (assembly)
  mutate(FacetLabel = "Unicycler Assembly Input") %>%
  ggplot(aes(x=InputContigCount,y=F1,colour = ToolName)) +
  geom_point(alpha=0.4) +
  geom_text(
    data = data.frame(FacetLabel = "Unicycler Assembly Input", ToolName = "PlaScope (assembly)", label = "No\nPredictions"), 
    aes(label   = label),
    x=I(0.5), #middle of plot
    y=I(0.5),
    colour = "grey45",
    size = 4
  ) +
  scale_colour_manual(values = plasmid.tool.colours) +
  theme_bw() +
  theme(legend.position = 'none') +
  labs(
    x = "Number of Contigs in Input Assembly",
    y = "F1 - Total Plasmid Content"
  ) +
  scale_x_log10(breaks = breaks, minor_breaks = minor_breaks,limits=c(10,1000)) +
  facet_nested(~FacetLabel + factor(ToolName,levels=c("HyAsp","MOB-suite","PLASMe","PlaScope (assembly)","Plasmer","PlasmidHunter","Platon")))
plot.AllPlasContigCount.F1.unicycler
```

Multipanel - don't include read based tools, not relevant
```{r}
ggarrange(
  plot.AllPlasContigCount.F1.spades,
  plot.AllPlasContigCount.F1.unicycler,
  nrow=2,
  labels = 'AUTO',
  align = 'hv'
)
#ggsave("Figures/SuppFigure15.pdf",dpi=300,units = 'cm',height = 17.5,width = 30)
```


auNGA

Correlation test

```{r}
quastMetricsTyping$spades %>%
  filter(QuastType == 'CombinedPlasmids', InputType == 'Assembly Based') %>%
  group_by(ToolName) %>%
  summarise(
    test = list(cor.test(F1,InputauNGA,method='spearman') %>% tidy())
  ) %>%
  unnest(test)
```

SPAdes plot

```{r}
breaks <- 10^(-10:10)
minor_breaks <- rep(1:9, 21)*(10^rep(-10:10, each=9))

plot.AllPlasauNGA.F1.spades <- quastMetricsTyping$spades %>%
  filter(QuastType == 'CombinedPlasmids',InputType=='Assembly Based') %>%
  mutate(FacetLabel = "SPAdes Assembly Input") %>%
  ggplot(aes(x=InputauNGA,y=F1,colour = ToolName)) +
  geom_point(alpha=0.4) +
  scale_colour_manual(values = plasmid.tool.colours) +
  theme_bw() +
  theme(legend.position = 'none',axis.text.x = element_text(angle=90,vjust=0.5,hjust=1)) +
  labs(
    x = "auNGA of Input Assembly",
    y = "F1 - Total Plasmid Content"
  ) +
    #scale_x_log10(breaks = breaks, minor_breaks = minor_breaks,limits=c(1,1000000)) +
  #xlim(0,250000) +
  facet_nested(~FacetLabel + factor(ToolName,levels=c("HyAsp","MOB-suite","PLASMe","PlaScope (assembly)","Plasmer","PlasmidHunter","Platon")))
plot.AllPlasauNGA.F1.spades
```

Unicycler plot

```{r}
breaks <- 10^(-10:10)
minor_breaks <- rep(1:9, 21)*(10^rep(-10:10, each=9))

plot.AllPlasauNGA.F1.unicycler <- quastMetricsTyping$unicycler %>%
  filter(QuastType == 'CombinedPlasmids',InputType=='Assembly Based',ToolName !='PlaScope (assembly)') %>%
  add_row(ToolName = "PlaScope (assembly)",F1=NA,InputType="Assembly Based") %>% #for adding PlaScope (assembly)
  mutate(FacetLabel = "Unicycler Assembly Input") %>%
  ggplot(aes(x=InputauNGA,y=F1,colour = ToolName)) +
  geom_point(alpha=0.4) +
  geom_text(
    data = data.frame(FacetLabel = "Unicycler Assembly Input", ToolName = "PlaScope (assembly)", label = "No\nPredictions"), 
    aes(label   = label),
    x=I(0.5), #middle of plot
    y=I(0.5),
    colour = "grey45",
    size = 4
  ) +
  scale_colour_manual(values = plasmid.tool.colours) +
  theme_bw() +
  theme(legend.position = 'none',axis.text.x = element_text(angle=90,vjust=0.5,hjust=1)) +
  labs(
    x = "auNGA of Input Assembly",
    y = "F1 - Total Plasmid Content"
  ) +
  #scale_x_log10(breaks = breaks, minor_breaks = minor_breaks,limits=c(1000,100000)) +
  #xlim(0,250000) +
  facet_nested(~FacetLabel + factor(ToolName,levels=c("HyAsp","MOB-suite","PLASMe","PlaScope (assembly)","Plasmer","PlasmidHunter","Platon")))
plot.AllPlasauNGA.F1.unicycler
```

Multipanel

```{r}
ggarrange(
  plot.AllPlasauNGA.F1.spades,
  plot.AllPlasauNGA.F1.unicycler,
  nrow=2,
  labels = 'AUTO',
  align = 'hv'
)
#ggsave("Figures/SuppFigure16.pdf",dpi=300,units = 'cm',height = 17.5,width = 30)
```


## Deadends against Performance

Correlation test - only assembly input tools

```{r}
quastMetricsTyping$spades %>%
  filter(QuastType == 'CombinedPlasmids', InputType == 'Assembly Based') %>%
  group_by(ToolName) %>%
  summarise(
    test = list(cor.test(F1,DeadendCount,method='spearman') %>% tidy())
  ) %>%
  unnest(test)
```

SPAdes plot

```{r}
breaks <- 10^(-10:10)
minor_breaks <- rep(1:9, 21)*(10^rep(-10:10, each=9))

plot.AllPlasDeadend.F1.spades <- quastMetricsTyping$spades %>%
  filter(QuastType == 'CombinedPlasmids',InputType=='Assembly Based') %>%
  mutate(FacetLabel = "SPAdes Assembly Input") %>%
  ggplot(aes(x=DeadendCount,y=F1,colour = ToolName)) +
  geom_point(alpha=0.4) +
  scale_colour_manual(values = plasmid.tool.colours) +
  theme_bw() +
  theme(legend.position = 'none') +
  labs(
    x = "Number of Deadends in Input Assembly Graph",
    y = "F1 - Total Plasmid Content"
  ) +
    scale_x_log10(breaks = breaks, minor_breaks = minor_breaks,limits=c(1,50000)) +
  facet_nested(~FacetLabel + factor(ToolName,levels=c("HyAsp","MOB-suite","PLASMe","PlaScope (assembly)","Plasmer","PlasmidHunter","Platon")))
plot.AllPlasDeadend.F1.spades
```

Unicycler plot

```{r}
breaks <- 10^(-10:10)
minor_breaks <- rep(1:9, 21)*(10^rep(-10:10, each=9))

plot.AllPlasDeadend.F1.unicycler <- quastMetricsTyping$unicycler %>%
  filter(QuastType == 'CombinedPlasmids',InputType=='Assembly Based',ToolName!='PlaScope (assembly)') %>%
  add_row(ToolName = "PlaScope (assembly)",F1=NA,InputType="Assembly Based") %>% #for adding PlaScope (assembly)
  mutate(FacetLabel = "Unicycler Assembly Input") %>%
  ggplot(aes(x=DeadendCount,y=F1,colour = ToolName)) +
  geom_point(alpha=0.4) +
  geom_text(
    data = data.frame(FacetLabel = "Unicycler Assembly Input", ToolName = "PlaScope (assembly)", label = "No\nPredictions"), 
    aes(label   = label),
    x=I(0.5), #middle of plot
    y=I(0.5),
    colour = "grey45",
    size = 4
  ) +
  scale_colour_manual(values = plasmid.tool.colours) +
  theme_bw() +
  theme(legend.position = 'none') +
  labs(
    x = "Number of Deadends in Input Assembly Graph",
    y = "F1 - Total Plasmid Content"
  ) +
    scale_x_log10(breaks = breaks, minor_breaks = minor_breaks,limits=c(1,50000)) +
  facet_nested(~FacetLabel + factor(ToolName,levels=c("HyAsp","MOB-suite","PLASMe","PlaScope (assembly)","Plasmer","PlasmidHunter","Platon")))
plot.AllPlasDeadend.F1.unicycler
```

Multipanel

```{r}
ggarrange(
  plot.AllPlasDeadend.F1.spades,
  plot.AllPlasDeadend.F1.unicycler,
  nrow=2,
  labels = 'AUTO',
  align = 'hv'
)
#ggsave("Figures/SuppFigure17.pdf",dpi=300,units = 'cm',height = 17.5,width = 32.5)
```

